### 2024-10-07 Article/Article.tex
update Article.tex

\documentclass[3p,times]{elsarticle}
\usepackage[utf8]{inputenc}

\usepackage{amssymb,amsmath,latexsym}
\usepackage{soul,color}
\usepackage{xcolor}
\usepackage{graphicx,amssymb,amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{pgfplots}
\usepackage{array}
\usepackage[utf8]{inputenc}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{tikz}
\usepackage{caption}
\setcounter{secnumdepth}{4}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{float}
\usepackage{subcaption}
\pgfplotsset{compat=newest}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{array}
\usepackage{graphicx}
%\usepackage{authblk}
\usepackage{multirow}

\usepackage[outdir=./]{epstopdf}
\usepackage{dblfloatfix}
\usepackage[figuresright]{rotating}

%\pagecolor[rgb]{0.25,0.25,0.25} %black
%\color[rgb]{0.9,0.9,0.9} %grey

\usepackage{ecrc}

\makeatletter %% <- make @ usable in command sequences
\newcount\SOUL@minus
\makeatother  %% <- revert @

%% The ecrc package defines commands needed for running heads and logos.
%% For running heads, you can set the journal name, the volume, the starting page and the authors

%% set the volume if you know. Otherwise `00'
\volume{00}

%% set the starting page if not 1
\firstpage{1}

\setlength{\textfloatsep}{5pt}
%% Give the name of the journal
\journalname{Computer Speech and Language}

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{Anidjar et al.}

%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo

%% Give the abbreviation of the Journal.
\jid{procs}

%% Give a short journal name for the dummy logo (if needed)
\jnltitlelogo{Speech Recognition}

%% Hereafter the template follows `elsarticle'.
%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.

%% Elsevier CRC generally uses a numbered reference style
%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
%% If using BibTeX, use the style file elsarticle-num.bst

%% End of ecrc-specific commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand\MyBox[2]{
  \fbox{\lower0.75cm
    \vbox to 1.7cm{\vfil
      \hbox to 1.7cm{\hfil\parbox{1.4cm}{#1\\#2}\hfil}
      \vfil}%
  }%
}

\begin{document}

\begin{frontmatter}

\title{Vision-Based Automatic Landing of Drones}

\author[a,b,c,d]{Or Haim Anidjar\corref{cor1}}
\ead{orhaim@ariel.ac.il}

\author[a]{Moria Grohar}
\ead{moriagro@gmail.com}

\author[a]{Shirel Turgeman}
\ead{shirel.zz10@gmail.com}

\author[a]{Adi Peisach}
\ead{adi.peisach@gmail.com}

\author[a, b, c]{Boaz Ben-Moshe}
\ead{benmo@ariel.ac.il}

\address[a]{School of Computer Science, Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}

\address[b]{Ariel Cyber Innovation Center, Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}

\address[c]{Kinematics and Computational Geometry Lab (K\&CG), Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}

\address[d]{Data Science and Artificial Intelligence Research Center, Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}

\cortext[cor1]{Corresponding author: Or Haim Anidjar, School of Computer Science, Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}

\begin{abstract}
This article introduces a platform designed to enable precise landings on the edge of rooftops, facilitating operations at boundary locations. The platform integrates voice recognition capabilities for activation, eliminating reliance on manual button controls. The primary objective is to develop a methodology and control algorithm that allows drones to guard settlements effectively. This research employs a combination of straight-line detection and object detection, avoiding the use of global positioning systems. The system is engineered to operate with drones equipped with existing cameras, obviating the need for additional sensors, and is implemented using the DJI SDK on Android devices. This paper presents a visual landing technology through a proposed algorithm, which is divided into two key tasks: scene evaluation and landing site security. Initially, the drone utilizes object detection to identify and avoid obstacles within the landing area, enabling autonomous descent planning. Once obstacles are cleared, the drone transitions to descent mode. For precise landings at the edge of a rooftop, an edge detection algorithm is employed alongside a target line selection process, allowing the user to designate a specific landing line beforehand, ensuring accuracy during the final approach.

\end{abstract}

\begin{keyword}
Visual-Based Landing; Autonomous Landing; Accurate Landing; Spoken Language Recognition.
\end{keyword}

\end{frontmatter}

\section{Introduction}
Unmanned aerial vehicles (UAVs), commonly known as drones, are aircraft that operate without an onboard pilot, controlled either through radio remote systems or autonomous onboard programs. Drones are valued for their simple yet effective design, ease of operation, flexibility, and cost-efficiency, making them versatile tools in both military and civilian domains. In military operations, they play crucial roles in tasks such as tactical reconnaissance, territorial surveillance, and target acquisition. On the civilian side, drones are utilized for activities like environmental monitoring, weather data collection, and infrastructure inspection. As drones become increasingly prevalent in both sectors, ensuring their safe operation—particularly during landing—has emerged as a critical concern.\\Autonomous drone operations have rapidly advanced, yet precision landing remains a significant challenge, especially in environments where GPS signals are unreliable or unavailable. GPS signals can be easily disrupted by various factors: (a) weather conditions and sunspots may weaken signals, although they typically do not hinder positioning; (b) electromagnetic interference from sources like radios and strong magnetic fields can cause varying degrees of disruption; (c) signal strength diminishes under shelters such as buildings, vehicles, insulation materials, trees, and metal components; and (d) high-rise buildings and dense urban areas can severely impact GPS signal quality. Traditional drone landing methods often rely on GPS, which proves inadequate in urban or indoor settings. This limitation poses significant challenges for applications requiring precise landings, such as urban package delivery, infrastructure inspection, and emergency response. As a result, there is a critical need to develop autonomous positioning and flight control systems for drones that do not rely on GPS signals.\\
This research addresses these challenges by developing a visual-based landing system that enhances accuracy and safety. Our approach enables drones to autonomously identify and land on planar surfaces, such as rooftops, relying solely on visual data from the onboard camera. By eliminating the need for additional sensors or external data inputs, this system offers a robust solution for autonomous landings in complex environments.

\subsection{Authors Contribution}
We propose a visual processing framework that enables the drone to autonomously land by utilizing object (obstacle) detection and edge detection. Our approach is tested on a DJI drone equipped with a standard camera, using the DJI SDK for implementation on Android devices. Additionally, we have implemented a "guard" mode in the app—a button that, when activated, is designed to detect movement (such as people, cars, etc.) and send alerts. The system's robustness is further enhanced by incorporating basic voice commands through a speech recognition module, meeting the requirements outlined by MAFAT.

\begin{figure}[htp]
    \centering
    \includegraphics[width=11.0cm]{Schematic_for_automatic_landing.png}
    \caption{Schematic for automatic landing.}
    \label{fig:Schematic_for_automatic_landing.}
\end{figure}

% \subsection{Paper Structure}
% This paper is structured as follows: Section \ref{sec:related} discusses related work in autonomous drone landing and visual navigation. Section \ref{sec:datasets} details the datasets used for testing and validation. Section \ref{sec:framework} describes the proposed framework, including the algorithms and implementation details. Section \ref{sec:exp_eval} presents the experimental evaluation and results. Finally, Section \ref{sec:discussion} offers a discussion on the findings, and Section \ref{sec:conclusions} concludes the paper with suggestions for future work.

% \begin{table}[th]
%   \caption{List of abbreviations}

%   \centering
%   \begin{tabular}{ |c|c|c|}
%   \hline
%     \multicolumn{1}{|c|}{\textbf{Abbreviation}} &
%     \multicolumn{1}{|c|}{\textbf{Meaning}}\\\hline
%     PID & \quad Proportional Integral Derivative \\\hline

%   \end{tabular}
%   \label{tab:list_of_abbreviations}
% \end{table}

\section{Related Work} \label{sec:related}
\subsection{Obstacle Avoidance}
Obstacle avoidance is a critical aspect of autonomous drone operations, especially in dynamic environments where both static and moving obstacles are present. One approach is integrating depth images with an occupancy voxel map to detect and track dynamic obstacles \cite{xu2023real}. This approach effectively balances computational efficiency with the need for accurate detection and tracking, making it suitable for real-time UAV operations. Another approach is.... \cite{redmon2017yolo9000}

% \cite{lee2022camera} is a set.

% Spoken language recognition (SLR) has been a

\section{Datasets} \label{sec:datasets}

In the field of speech recognition, the ability to accurately transcribe

\section{Framework} \label{sec:framework}

\section{Experimental Evaluation and Results} \label{sec:exp_eval}

In accordance with the methodologies outlined in the framework, several modifications were independently evaluated. Below is a tabulated comparison illustrating the differences among these variations, as in Table~\ref{tab:results_comparison}:

\begin{table}[ht]
\centering
\caption{Comparative Analysis of Model Improvements on Validation Dataset.}
\label{tab:results_comparison}
\resizebox{0.4\textwidth}{!}{%
\begin{tabular}{|c|c|}
\hline
\textbf{Model} & \textbf{Accuracy} \\
\hline
Baseline & 0.54 \\

\hline
\end{tabular}%
}
\end{table}

Figure~\ref{fig:conf_matrix_test} depicting the confusion matrices for the final model on :

\begin{figure}[htp]
    \centering
    \includegraphics[width=11.0cm]{con_matrix_test.jpeg}
    \caption{Confusion Matrix on Validation Dataset for the Final Model, showing minimal error.}
    \label{fig:conf_matrix_test}
\end{figure}

The results in Eq.(\ref{eq:inequality}) clearly demonstrate that Boaz has no idea in equations.

\begin{equation} \label{eq:inequality}
    3 \neq 3
\end{equation}

\section{Discussion} \label{sec:discussion}

Advancements in language recognition technologies have been noteworthy, yet they confront several challenges and limitations. This discussion highlights some of the prevalent issues:

\begin{enumerate}

    \item \textbf{Linguistic Ambiguity.} Distinguishing between languages with shared linguistic traits

    \item \textbf{Code-Switching Phenomenon.} In multilingual settings,

\end{enumerate}

\section{Conclusions and Future Work} \label{sec:conclusions}

In this study, we have

% \bibliographystyle{model5-names}\biboptions{authoryear}
% \bibliography{main}
\bibliographystyle{plain}
\bibliography{myDoc}
\end{document}

### 2024-10-07 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java
Adding record using voice commands and detect hazards before landing

@@ -106,7 +106,7 @@ public class ControllerImageDetection {
     private Runnable toggleMovementDetection;
     private Button edgeDetect;
     private double initialDistance = 0;  // Store the original distance when the movement starts
-    private double velocity = 0.01;      // Start with an initial velocity of 0.01
+    private double velocity = 0.02;      // Start with an initial velocity of 0.01
     private double accelerationRate = 0.01;  // Fixed rate of velocity increase/decrease
 
     //constructor
@@ -256,7 +256,11 @@ public class ControllerImageDetection {
         if (closestLine != null) {
             selectedLine = closestLine;
             lineSelected = true;
+
+            // Store the original line properties
+            trackLine.storeOriginalLineProperties(selectedLine);
         }
+
     }
 
     public void setCurrentImage(Bitmap frame, double[] pos) {
@@ -291,9 +295,7 @@ public class ControllerImageDetection {
 
         double droneRelativeHeight = dataFromDrone.getAltitudeBelow();
         boolean isUltrasonicBeingUsed = dataFromDrone.isUltrasonicBeingUsed();
-        if (droneRelativeHeight <= 0f
-            //|| dataFromDrone.getGPS().getAltitude() <= 0.2f
-        ) {
+        if (droneRelativeHeight <= 0f) {
             showToast("Land2!!!!");
             throttle_pid.reset();
             pitch_pid.reset();
@@ -455,7 +457,7 @@ public class ControllerImageDetection {
 
     private ControlCommand buildControlCommandEdgeFixedVelocity(double dyReal, double dt, Mat imgToProcess) {
         double maxSpeed = 1.0;   // Cap the maximum velocity
-        double minSpeed = 0.01;  // Minimum starting velocity
+        double minSpeed = 0.02;  // Minimum starting velocity
 
         // Set initial distance only at the start of the movement
         if (initialDistance == 0) {
@@ -489,8 +491,8 @@ public class ControllerImageDetection {
             showToast("Stopping, distance reached!");
             velocity = 0;  // Stop the drone
             initialDistance = 0;  // Reset for the next movement
-            t = -0.1f;
-            error_y = 0.1;
+            t = -0.08f;
+            error_y = 0.08;
         } else {
             t = 0;
         }
@@ -523,7 +525,7 @@ public class ControllerImageDetection {
     private ControlCommand buildControlCommandEdge(double dyReal, double dt, Mat imgToProcess) {
[…]

### 2024-10-07 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/HandleSpeechToText.java

@@ -11,17 +11,30 @@ import com.dji.sdk.sample.demo.speechToText.SpeechToText;
 
 public class HandleSpeechToText {
     private final SpeechToText speechToText;
-    private final Runnable goToFunc, goToFMM_btn, stopButton, takeOff, edgeDetect, upButton, downButton, landButton;
+    private final Runnable goToFunc,
+            startRecording, stopRecording,
+            stopButton, takeOff, edgeDetect, upButton, downButton, landButton, movementDetectedStart, movementDetectedEnd;
     protected ImageView audioIcon;
 
-    //context, audioIcon, goToFMM_btn, stopButton, takeOff, this::goToFunc
-    public HandleSpeechToText(Context context, ImageView audioIcon, Runnable goToFMM_btn, Runnable stopButton,
-                              Runnable takeOff, Runnable goToFunc, Runnable edgeDetect, Runnable upButton, Runnable downButton, Runnable landButton
+    public HandleSpeechToText(Context context,
+                              ImageView audioIcon,
+                              Runnable stopButton,
+                              Runnable takeOff,
+                              Runnable goToFunc,
+                              Runnable edgeDetect,
+                              Runnable upButton,
+                              Runnable downButton,
+                              Runnable landButton,
+                              Runnable startRecording,
+                              Runnable stopRecording,
+                              Runnable movementDetectedStart,
+                              Runnable movementDetectedEnd
     ) {
         speechToText = new SpeechToText(context, this::performActionOnResults, null, this::updateStartListening);
         speechToText.startListening();
         this.audioIcon = audioIcon;
-        this.goToFMM_btn = goToFMM_btn;
+        this.startRecording = startRecording;
+        this.stopRecording = stopRecording;
         this.stopButton = stopButton;
         this.takeOff = takeOff;
         this.goToFunc = goToFunc;
@@ -29,6 +42,8 @@ public class HandleSpeechToText {
         this.upButton = upButton;
         this.downButton = downButton;
         this.landButton = landButton;
+        this.movementDetectedStart = movementDetectedStart;
+        this.movementDetectedEnd = movementDetectedEnd;
     }
 
     public void updateStartListening() {
@@ -39,41 +54,73 @@ public class HandleSpeechToText {
     @SuppressLint("UseCompatLoadingForDrawables")
     public void performActionOnResults(String text) {
         showToast(text);
+        text = text.toLowerCase();
 
-        if (text.contains("go to")) {
+        // Movement Commands
+        if (containsAny(text, "go to")) {
             showToast("go to");
[…]

### 2024-10-07 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/TrackLine.java

@@ -23,8 +23,21 @@ public class TrackLine {
     MatOfPoint selectedLineFeatures;
     MatOfPoint2f prevPoints, currPoints;
     Mat previousImage = null;
+    // Variables to store original line properties
+    private double originalLineLength;
+    private double originalSlope;
 
     public TrackLine() {
+    }
+
+    // Calculate and store original line length and slope when selecting the line
+    public void storeOriginalLineProperties(Point[] selectedLine) {
+        // Calculate the length of the selected line
+        originalLineLength = Math.sqrt(Math.pow(selectedLine[1].x - selectedLine[0].x, 2) +
+                Math.pow(selectedLine[1].y - selectedLine[0].y, 2));
+
+        // Calculate the slope of the selected line
+        originalSlope = (selectedLine[1].y - selectedLine[0].y) / (selectedLine[1].x - selectedLine[0].x);
     }
 
     // Detect features along the selected line

### 2024-10-08 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ALRemoteControllerView.java
strict recognition of the line including only horizontal line + fit line better

@@ -616,7 +616,7 @@ public class ALRemoteControllerView extends RelativeLayout
     // Toggle the movement detection process
     private void toggleMovementDetectionStart() {
 
-        gimbalController.rotateGimbalToDegree(0);
+//        gimbalController.rotateGimbalToDegree(0);
         // Start movement detection
         isMovementDetectionRunning = true;
         movementDetector.setOriginalImage(convertBitmapToMat(droneIMG));  // Set the initial frame

### 2024-10-08 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java

@@ -29,6 +29,7 @@ import org.opencv.imgcodecs.Imgcodecs;
 import org.opencv.imgproc.Imgproc;
 
 import java.util.ArrayList;
+import java.util.Arrays;
 import java.util.HashMap;
 import java.util.List;
 import java.util.Map;
@@ -250,16 +251,18 @@ public class ControllerImageDetection {
 //        boolean isUltrasonicBeingUsed = dataFromDrone.isUltrasonicBeingUsed();
         List<Object[]> pointArr = EdgeDetection.detectLines(imgToProcess, droneRelativeHeight);
         Point[] closestLine = selectBestLinePoint(pointArr);
-        trackLine.detectLineFeatures(closestLine, imgToProcess);
+        showToast(Arrays.toString(closestLine));
 
         // Store the closest line as the selected line and mark that a line has been selected
         if (closestLine != null) {
             selectedLine = closestLine;
             lineSelected = true;
+            Imgproc.line(imgToProcess, closestLine[0], closestLine[1], new Scalar(255, 0, 0), 3, Imgproc.LINE_AA, 0);
 
             // Store the original line properties
             trackLine.storeOriginalLineProperties(selectedLine);
         }
+        trackLine.detectLineFeatures(closestLine, imgToProcess);
 
     }
 
@@ -299,7 +302,8 @@ public class ControllerImageDetection {
             showToast("Land2!!!!");
             throttle_pid.reset();
             pitch_pid.reset();
-            flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
+            flightControlMethods.land(this::stopEdgeDetection, null);
+//            flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
             return null;
         }
         if (currentLine == null) {
@@ -310,7 +314,8 @@ public class ControllerImageDetection {
                 showToast("Land2!!!!");
                 throttle_pid.reset();
                 pitch_pid.reset();
-                flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
+//                flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
+                flightControlMethods.land(this::stopEdgeDetection, null);
                 return null;
             } else {
                 return stayOnPlace();
@@ -344,6 +349,7 @@ public class ControllerImageDetection {
             if (!lineSelected) {
                 findClosestLine(imgToProcess);
                 frameCount = 0;
+                return;
             }
[…]

### 2024-10-08 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/EdgeDetection.java

@@ -15,8 +15,8 @@ import java.util.List;
 public class EdgeDetection {
 
     private static final int edgeThreshold = 150;
-    private static final int threshold1 = 170; //200;//170;
-    private static final int threshold2 = 280; //300;//280;
+    private static final int threshold1 = 200; //200;//170;
+    private static final int threshold2 = 300; //300;//280;
     private static final int apertureSize = 3;
     // adjust the maximum number of found lines in the image
     private static final int maxLines = 5;
@@ -51,16 +51,18 @@ public class EdgeDetection {
             double thetaDegrees = Math.toDegrees(theta);
 
             // Determine if the line is horizontal (within 30 degrees of the x-axis)
-            boolean isHorizontal = (Math.abs(thetaDegrees) <= 30) || (thetaDegrees >= 150 && thetaDegrees <= 180);
+            boolean isHorizontal = !((Math.abs(thetaDegrees) <= 30) || (thetaDegrees >= 150 && thetaDegrees <= 180));
 
 
             double a = Math.cos(theta), b = Math.sin(theta);
             double x0 = a * rho, y0 = b * rho;
             Point pt1 = new Point(Math.round(x0 + 1000 * (-b)), Math.round(y0 + 1000 * (a)));
             Point pt2 = new Point(Math.round(x0 - 1000 * (-b)), Math.round(y0 - 1000 * (a)));
+            if (isHorizontal) {
+                pointList.add(new Object[]{new Point[]{pt1, pt2}, isHorizontal});
 
-            pointList.add(new Object[]{new Point[]{pt1, pt2}, isHorizontal});
-            Imgproc.line(input, pt1, pt2, new Scalar(0, 0, 255), 3, Imgproc.LINE_AA, 0);
+                Imgproc.line(input, pt1, pt2, new Scalar(0, 0, 255), 3, Imgproc.LINE_AA, 0);
+            }
         }
 
         if (pointList.size() == 0 && droneHeight <= 0.2) {
@@ -124,7 +126,7 @@ public class EdgeDetection {
             double thetaDegrees = Math.toDegrees(theta);
 
             // Determine if the line is horizontal (within 30 degrees of the x-axis)
-            boolean isHorizontal = (Math.abs(thetaDegrees) <= 30) || (thetaDegrees >= 150 && thetaDegrees <= 180);
[…]

### 2024-10-08 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/TrackLine.java

@@ -1,5 +1,7 @@
 package com.dji.sdk.sample.demo.accurateLandingController;
 
+import static com.dji.sdk.sample.internal.utils.ToastUtils.showToast;
+
 import org.opencv.core.Core;
 import org.opencv.core.CvType;
 import org.opencv.core.Mat;
@@ -15,6 +17,7 @@ import org.opencv.imgproc.Imgproc;
 import org.opencv.video.Video;
 
 import java.util.ArrayList;
+import java.util.Arrays;
 import java.util.List;
 
 public class TrackLine {
@@ -50,8 +53,8 @@ public class TrackLine {
 
         Mat grayImage = new Mat();
         Imgproc.cvtColor(image, grayImage, Imgproc.COLOR_BGR2GRAY);
-        Imgproc.goodFeaturesToTrack(grayImage, selectedLineFeatures, 200, 0.03, 5, mask);
-
+        Imgproc.goodFeaturesToTrack(grayImage, selectedLineFeatures, 150, 0.05, 10, mask);
+        showToast(Arrays.toString(selectedLineFeatures.toArray()));
         // Convert features to a format suitable for optical flow
         prevPoints = new MatOfPoint2f(selectedLineFeatures.toArray());
 
@@ -111,7 +114,7 @@ public class TrackLine {
     // Helper function to create a mask around the selected line
     private Mat createLineMask(Point[] selectedLine, Size imageSize) {
         Mat mask = Mat.zeros(imageSize, CvType.CV_8U);
-        Imgproc.line(mask, selectedLine[0], selectedLine[1], new Scalar(255), 5); // Adjust thickness
+        Imgproc.line(mask, selectedLine[0], selectedLine[1], new Scalar(255), 10); // Adjust thickness
         return mask;
     }
 

### 2024-10-08 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java
moving code to a different function

@@ -299,23 +299,13 @@ public class ControllerImageDetection {
         double droneRelativeHeight = dataFromDrone.getAltitudeBelow();
         boolean isUltrasonicBeingUsed = dataFromDrone.isUltrasonicBeingUsed();
         if (droneRelativeHeight <= 0f) {
-            showToast("Land2!!!!");
-            throttle_pid.reset();
-            pitch_pid.reset();
-            flightControlMethods.land(this::stopEdgeDetection, null);
-//            flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
+            autoLand("Land2!!!!");
             return null;
         }
         if (currentLine == null) {
             Log.i("EdgeDetect", isUltrasonicBeingUsed + ": rh: " + droneRelativeHeight + ", h:" + dataFromDrone.getGPS().getAltitude());
-            if (droneRelativeHeight <= 0.2f
-                //|| dataFromDrone.getGPS().getAltitude() <= 0.2f
-            ) {
-                showToast("Land2!!!!");
-                throttle_pid.reset();
-                pitch_pid.reset();
-//                flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
-                flightControlMethods.land(this::stopEdgeDetection, null);
+            if (droneRelativeHeight <= 0.2f) {
+                autoLand("Land3!!!!");
                 return null;
             } else {
                 return stayOnPlace();
@@ -333,6 +323,14 @@ public class ControllerImageDetection {
 
         updateLog(command, 1, selectedLine, dyRealPitch);
         return command;
+    }
+
+    public void autoLand(String message) {
+        showToast(message);
+        throttle_pid.reset();
+        pitch_pid.reset();
+//                flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
+        flightControlMethods.land(this::stopEdgeDetection, null);
     }
 
     public void processImage(Bitmap frame, double droneHeight) {
@@ -361,15 +359,8 @@ public class ControllerImageDetection {
             Log.e("Error: ", Objects.requireNonNull(e.getMessage()));
             showToast(Objects.requireNonNull(e.getMessage()));
             double droneRelativeHeight = dataFromDrone.getAltitudeBelow();
-            if (droneRelativeHeight <= 0.2f
-                //|| dataFromDrone.getGPS().getAltitude() <= 0.2f
-            ) {
-                showToast("LandError!!!!");
-                throttle_pid.reset();
-                pitch_pid.reset();
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ALRemoteControllerView.java
Fixing tracking line recognition

@@ -307,10 +307,11 @@ public class ALRemoteControllerView extends RelativeLayout
         if (!isRecording) {
             isRecording = true;
             recordVideo.startRecording();
-
+            recordBtn.setBackgroundColor(Color.GREEN);
         } else {
             isRecording = false;
             recordVideo.stopRecording();
+            recordBtn.setBackgroundColor(Color.WHITE);
         }
     }
 
@@ -450,14 +451,16 @@ public class ALRemoteControllerView extends RelativeLayout
     }
 
     private void accurateLanding() {
-        boolean isEdgeDetect = !controllerImageDetection.isEdgeDetectionMode();
-        if (isEdgeDetect || !controllerImageDetection.isObjectDetecting()) {
-            edgeDetect.setBackgroundColor(Color.GREEN);
-        } else {
+        if (controllerImageDetection.isObjectDetecting()) {
             edgeDetect.setBackgroundColor(Color.WHITE);
+            controllerImageDetection.stopObjectDetectionAlgo();
+        } else if (controllerImageDetection.isEdgeDetectionMode()) {
+            edgeDetect.setBackgroundColor(Color.WHITE);
+            controllerImageDetection.setEdgeDetectionMode(false);
+        } else {
+            edgeDetect.setBackgroundColor(Color.GREEN);
+            startObjectDetectionAlgo();
         }
-        startObjectDetectionAlgo();
-//        controllerImageDetection.setEdgeDetectionMode(isEdgeDetect);
     }
 
     public void upButton() {
@@ -597,7 +600,7 @@ public class ALRemoteControllerView extends RelativeLayout
 //                break;
 
             case R.id.gimbal_pitch_update:
-//                ToastUtils.setResultToToast(String.valueOf(Float.parseFloat(gimbal.getText().toString())));
+                showToast(String.valueOf(Float.parseFloat(gimbal.getText().toString())));
                 gimbalController.rotateGimbalToDegree(Float.parseFloat(gimbal.getText().toString()));
 
 

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java

@@ -46,6 +46,8 @@ public class ControllerImageDetection {
     private final DataFromDrone dataFromDrone;
     //    Double PP = 0.5, II = 0.02, DD = 0.01, MAX_I = 0.5;
     Double PP = 0.05, II = 0.02, DD = 0.01, MAX_I = 0.5;
+//    Double PP = 0.1, II = 0.01, DD = 0.05, MAX_I = 1.0;
+
     private ImageView imageView;  // ImageView to display the frames
     private boolean isPlaying = false;  // To control the video playback
     private boolean isDetectingPlane = false;
@@ -53,7 +55,7 @@ public class ControllerImageDetection {
     private boolean isObjectDetecting = false;
     private Handler handler = new Handler(Looper.getMainLooper());  // For updating the UI
     private Python python;
-    private double focal_length = 4.8; // Field of View in mm
+    private double focal_length = 4.5; // Field of View in mm
     private double sensor_width = 6.4;  // Sensor width in millimeters (approximate for 1/2" CMOS sensor)
     private ArrayList<Bitmap> imageList = new ArrayList<>();
     private PyObject PlaneHandlerClass;
@@ -107,7 +109,7 @@ public class ControllerImageDetection {
     private Runnable toggleMovementDetection;
     private Button edgeDetect;
     private double initialDistance = 0;  // Store the original distance when the movement starts
-    private double velocity = 0.02;      // Start with an initial velocity of 0.01
+    private double velocity = 0.01;      // Start with an initial velocity of 0.01
     private double accelerationRate = 0.01;  // Fixed rate of velocity increase/decrease
 
     //constructor
@@ -126,15 +128,21 @@ public class ControllerImageDetection {
         this.gimbalController = gimbalController;
         this.imageView = imageView;  // Initialize the ImageView
 
-        //Do we need it
-        this.frameWidth = 640;
-        this.frameHeight = 480;
-        this.trackLine = new TrackLine();
+//        //Do we need it?
+//        this.frameWidth = 640;
+//        this.frameHeight = 480;
+        this.trackLine = new TrackLine(context);
 
         initPIDs(p, i, d, max_i, "roll");
         initPIDs(p, i, d, max_i, "pitch");
         initPIDs(p, i, d, max_i, "throttle");
         setDescentRate(t);
+    }
+
+    private static double calculateOptimalVelocity(double distance, double maxSpeed) {
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/RecordVideo.java

@@ -1,4 +1,6 @@
 package com.dji.sdk.sample.demo.accurateLandingController;
+
+import android.util.Log;
 import android.view.View;
 import android.widget.ImageView;
 
@@ -8,20 +10,29 @@ import com.dji.sdk.sample.internal.utils.ToastUtils;
 
 import dji.common.camera.SettingsDefinitions;
 
-public class RecordVideo{
-    private ImageView recIcon;
+public class RecordVideo {
+    private final ImageView recIcon;
+
     public RecordVideo(ImageView recIcon) {
         onStart();
         this.recIcon = recIcon;
     }
 
-    protected void onStart() {
+    public void onStart() {
 
         if (ModuleVerificationUtil.isCameraModuleAvailable()) {
             DJISampleApplication.getProductInstance()
                     .getCamera()
                     .setMode(SettingsDefinitions.CameraMode.RECORD_VIDEO,
-                            djiError -> ToastUtils.setResultToToast("SetCameraMode to recordVideo"));
+                            djiError -> {
+                                //success so, start recording
+                                if (null == djiError) {
+                                    ToastUtils.setResultToToast("SetCameraMode to recordVideo");
+                                } else {
+                                    ToastUtils.setResultToToast(djiError.getDescription());
+                                    Log.i("videoError:", djiError.getDescription());
+                                }
+                            });
         }
     }
 
@@ -30,13 +41,21 @@ public class RecordVideo{
             DJISampleApplication.getProductInstance()
                     .getCamera()
                     .setMode(SettingsDefinitions.CameraMode.SHOOT_PHOTO,
-                            djiError -> ToastUtils.setResultToToast("SetCameraMode to shootPhoto"));
+                            djiError -> { //success so, start recording
+                                if (null == djiError) {
+                                    ToastUtils.setResultToToast("SetCameraMode to shootPhoto");
+                                } else {
+                                    ToastUtils.setResultToToast(djiError.getDescription());
+                                    Log.i("videoError:", djiError.getDescription());
+                                }
+                            });
         }
+
     }
 
-    protected void startRecording() {
+    public void startRecording() {
         recIcon.setVisibility(View.VISIBLE);
-
+        ToastUtils.setResultToToast(String.valueOf(ModuleVerificationUtil.isCameraModuleAvailable()));
         if (ModuleVerificationUtil.isCameraModuleAvailable()) {
             DJISampleApplication.getProductInstance()
                     .getCamera()
@@ -44,18 +63,30 @@ public class RecordVideo{
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/TrackLine.java

@@ -1,6 +1,14 @@
 package com.dji.sdk.sample.demo.accurateLandingController;
 
+import static com.dji.sdk.sample.demo.accurateLandingController.ALRemoteControllerView.TAG;
 import static com.dji.sdk.sample.internal.utils.ToastUtils.showToast;
+
+import static org.opencv.android.Utils.matToBitmap;
+
+import android.content.Context;
+import android.graphics.Bitmap;
+import android.os.Environment;
+import android.util.Log;
 
 import org.opencv.core.Core;
 import org.opencv.core.CvType;
@@ -16,6 +24,10 @@ import org.opencv.core.Size;
 import org.opencv.imgproc.Imgproc;
 import org.opencv.video.Video;
 
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.FileOutputStream;
+import java.io.IOException;
 import java.util.ArrayList;
 import java.util.Arrays;
 import java.util.List;
@@ -26,11 +38,18 @@ public class TrackLine {
     MatOfPoint selectedLineFeatures;
     MatOfPoint2f prevPoints, currPoints;
     Mat previousImage = null;
+    // Define tolerances for slope and distance
+    private static final double TOLERANCE_SLOPE = 0.1; // Adjust as necessary
+    private static final double TOLERANCE_DISTANCE = 5.0; // Adjust as necessary
+
     // Variables to store original line properties
     private double originalLineLength;
     private double originalSlope;
+    private Context context;
 
-    public TrackLine() {
+
+    public TrackLine(Context context) {
+        this.context = context;
     }
 
     // Calculate and store original line length and slope when selecting the line
@@ -53,7 +72,7 @@ public class TrackLine {
 
         Mat grayImage = new Mat();
         Imgproc.cvtColor(image, grayImage, Imgproc.COLOR_BGR2GRAY);
-        Imgproc.goodFeaturesToTrack(grayImage, selectedLineFeatures, 150, 0.05, 10, mask);
+        Imgproc.goodFeaturesToTrack(grayImage, selectedLineFeatures, 200, 0.03, 5, mask);
         showToast(Arrays.toString(selectedLineFeatures.toArray()));
         // Convert features to a format suitable for optical flow
         prevPoints = new MatOfPoint2f(selectedLineFeatures.toArray());
@@ -62,8 +81,48 @@ public class TrackLine {
         previousImage = image;
     }
 
+    public void saveImage(Bitmap bitmap) {
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/camera/RecordVideoView.java

@@ -1,6 +1,7 @@
 package com.dji.sdk.sample.demo.camera;
 
 import android.content.Context;
+import android.util.Log;
 
 import com.dji.sdk.sample.R;
 import com.dji.sdk.sample.internal.controller.DJISampleApplication;
@@ -43,7 +44,14 @@ public class RecordVideoView extends BaseThreeBtnView {
                             new CommonCallbacks.CompletionCallback() {
                                 @Override
                                 public void onResult(DJIError djiError) {
-                                    ToastUtils.setResultToToast("SetCameraMode to recordVideo");
+                                    if (djiError != null) {
+                                        ToastUtils.setResultToToast(djiError.getDescription());
+                                        Log.i("videoError:", djiError.getDescription());
+                                    } else {
+
+                                        ToastUtils.setResultToToast("SetCameraMode to recordVideo");
+                                    }
+
                                 }
                             });
         }
@@ -60,7 +68,13 @@ public class RecordVideoView extends BaseThreeBtnView {
                             new CommonCallbacks.CompletionCallback() {
                                 @Override
                                 public void onResult(DJIError djiError) {
-                                    ToastUtils.setResultToToast("SetCameraMode to shootPhoto");
+                                    if (djiError != null) {
+                                        ToastUtils.setResultToToast(djiError.getDescription());
+                                        Log.i("videoError:", djiError.getDescription());
+                                    } else {
+
+                                        ToastUtils.setResultToToast("SetCameraMode to shootPhoto");
+                                    }
                                 }
                             });
         }
@@ -114,6 +128,9 @@ public class RecordVideoView extends BaseThreeBtnView {
                                         changeDescription(time);
                                     }
                                 }, 0, 1);
+                            } else {
+                                ToastUtils.setResultToToast(djiError.getDescription());
+                                Log.i("videoError:", djiError.getDescription());
                             }
                         }
                     });
@@ -129,10 +146,15 @@ public class RecordVideoView extends BaseThreeBtnView {
                     .stopRecordVideo(new CommonCallbacks.CompletionCallback() {
                         @Override
                         public void onResult(DJIError djiError) {
-                            ToastUtils.setResultToToast("StopRecord");
-                            changeDescription("00:00:00");
-                            timer.cancel();
-                            timeCounter = 0;
+                            if (djiError == null) {
+                                ToastUtils.setResultToToast("StopRecord");
+                                changeDescription("00:00:00");
+                                timer.cancel();
+                                timeCounter = 0;
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java
new calculation to move drone

@@ -40,7 +40,7 @@ public class ControllerImageDetection {
 
     // depth map python view
 
-    private static final String TAG = ControllerImageDetection_copy.class.getSimpleName();
+    private static final String TAG = ControllerImageDetection.class.getSimpleName();
     private final int displayFps = 0;
     private final DataFromDrone dataFromDrone;
     //    Double PP = 0.5, II = 0.02, DD = 0.01, MAX_I = 0.5;
@@ -89,15 +89,10 @@ public class ControllerImageDetection {
     private Context context;
     private int frameHeight, frameWidth;
     private GimbalController gimbalController;
-
-
     private float lastP = 0, lastR = 0; // previous error
-
     private float r, gp = 0;
     private float p = 0.5f, i = 0.02f, d = 0.01f, max_i = 1, t = -0.6f;//t fot vertical throttle
-
     private double error_x, error_y;
-
     private double pitch = 0.0, roll = 0.0, alt = 0.0, dt = 0.0;
     private boolean activate = false;
     private TrackLine trackLine;
@@ -108,9 +103,22 @@ public class ControllerImageDetection {
     private double initialDistance = 0;  // Store the original distance when the movement starts
     private double velocity = 0.02;      // Start with an initial velocity of 0.01
     private double accelerationRate = 0.01;  // Fixed rate of velocity increase/decrease
+    private LandingAlgorithm landingAlgorithm;
+    private VLD_PID pitchPID;
+    private VLD_PID throttlePID;
+    private double fieldOfView = 84.0;  // Camera's horizontal field of view in degrees
+    private int imageWidth = 640;  // Width of the camera feed in pixels
+    private int imageHeight = 480;  // Width of the camera feed in pixels
 
     //constructor
-    public ControllerImageDetection(DataFromDrone dataFromDrone, FlightControlMethods flightControlMethods, Context context, ImageView imageView, GimbalController gimbalController, YoloDetector yoloDetector, Runnable toggleMovementDetection, Button edgeDetect) {
+    public ControllerImageDetection(DataFromDrone dataFromDrone,
+                                    FlightControlMethods flightControlMethods,
+                                    Context context,
+                                    ImageView imageView,
+                                    GimbalController gimbalController,
+                                    YoloDetector yoloDetector,
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/LandingAlgorithm.java

@@ -1,0 +1,59 @@
+package com.dji.sdk.sample.demo.accurateLandingController;
+
+import org.opencv.core.Mat;
+import org.opencv.core.Point;
+import org.opencv.core.Scalar;
+import org.opencv.imgproc.Imgproc;
+import com.dji.sdk.sample.demo.kcgremotecontroller.VLD_PID;
+
+
+public class LandingAlgorithm {
+
+    private double targetDistance = 0.03;  // Target distance of 3 cm before the line
+    private double currentVelocity = 0.01;  // Starting velocity
+    private double maxVelocity = 1.0;  // Cap the maximum velocity
+    private double minVelocity = 0.005;  // Minimum safe velocity
+    private double accelerationRate = 0.02;  // Rate to increase velocity
+    private double decelerationThreshold = 0.1;  // Distance where deceleration begins
+    private double initialDistance = 0;  // Stores initial distance to the line
+
+    private VLD_PID pitchPID;
+    private VLD_PID throttlePID;
+
+    // Constructor to initialize VLD_PID objects
+    public LandingAlgorithm(VLD_PID pitchPID, VLD_PID throttlePID) {
+        this.pitchPID = pitchPID;
+        this.throttlePID = throttlePID;
+    }
+
+    public ControlCommand approachLine(double dyReal, double dt, Mat imgToProcess) {
+
+        if (initialDistance == 0) {
+            initialDistance = Math.abs(dyReal);
+        }
+
+        double currentDistance = Math.abs(dyReal);
+        if (currentDistance > targetDistance) {
+            if (currentDistance > decelerationThreshold) {
+                currentVelocity = Math.min(currentVelocity + accelerationRate, maxVelocity);
+            } else {
+                currentVelocity = Math.max(currentVelocity - accelerationRate, minVelocity);
+            }
+
+            float pitchCommand = (float) pitchPID.update(currentVelocity, dt, maxVelocity);
+            float throttleCommand = (float) throttlePID.update(0, dt, maxVelocity);
+
+            Imgproc.putText(imgToProcess, "Distance to Line: " + currentDistance, new Point(imgToProcess.cols() / 2.0, imgToProcess.rows() / 2.0),
+                    Imgproc.FONT_HERSHEY_SIMPLEX, 1, new Scalar(0, 255, 0), 2);
+
+            return new ControlCommand(pitchCommand, 0, throttleCommand);
+        } else {
+            initialDistance = 0;  // Reset for next movement
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java
new calculation to move drone (3)

@@ -343,6 +343,42 @@ public class ControllerImageDetection {
 //        return command;
 //    }
 
+    public ControlCommand alignAndLand(Mat imgToProcess) {
+        long currTime = System.currentTimeMillis();
+        double dt = (currTime - prevTime) / 1000.0;
+        prevTime = currTime;
+
+        // Detect the line and get the center of the line segment
+        Point[] detectedLine = trackLine.trackSelectedLineUsingOpticalFlow(imgToProcess);
+        if (detectedLine == null) {
+            return stayOnPlace();  // Hover if no line is detected
+        }
+
+        // Calculate vertical distance to center the line horizontally in the image
+        double lineCenterY = (detectedLine[0].y + detectedLine[1].y) / 2.0;
+        double centerY = imageHeight / 2.0;
+        double yOffset = lineCenterY - centerY;
+
+        // If the line is centered vertically within a small threshold
+        if (Math.abs(yOffset) < 5) {
+            // Move forward by the distance equal to the altitude and land
+            double altitude = dataFromDrone.getAltitudeBelow();
+            showToast("Moving forward by altitude distance and landing.");
+            ControlCommand moveForwardCommand = landingAlgorithm.moveForwardByDistance(altitude, dt, imgToProcess);
+
+            if (moveForwardCommand.getPitch() == 0 && moveForwardCommand.getRoll() == 0 && moveForwardCommand.getVerticalThrottle() == 0) {
+                flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
+                return null;
+            }
+
+            return moveForwardCommand;
+        } else {
+            // Move vertically to align the line in the center
+            ControlCommand alignCommand = landingAlgorithm.verticalAlign(yOffset, dt, imgToProcess);
+            return alignCommand;
+        }
+    }
+
     public ControlCommand moveDroneToLine_sh(Mat imgToProcess) {
         long currTime = System.currentTimeMillis();
         double dt = (currTime - prevTime) / 1000.0;
@@ -370,7 +406,7 @@ public class ControllerImageDetection {
     private double calculateDistanceToLine(Point[] line) {
         Point start = line[0];
         Point end = line[1];
-        Point dronePosition = new Point(imageWidth / 2, imageHeight);
+        Point dronePosition = new Point(imageWidth / 2, imageHeight/2);
 
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/LandingAlgorithm.java

@@ -26,6 +26,25 @@ public class LandingAlgorithm {
         this.throttlePID = throttlePID;
     }
 
+    public ControlCommand moveForwardByDistance(double distance, double dt, Mat imgToProcess) {
+        double currentDistance = Math.abs(distance);
+        if (currentDistance > 0.05) {  // Stop when close enough (5 cm tolerance)
+            float pitchCommand = (float) pitchPID.update(currentDistance, dt, 1.0);
+            Imgproc.putText(imgToProcess, "Moving Forward by " + currentDistance, new Point(imgToProcess.cols() / 2.0, imgToProcess.rows() / 2.0),
+                    Imgproc.FONT_HERSHEY_SIMPLEX, 1, new Scalar(0, 255, 0), 2);
+            return new ControlCommand(pitchCommand, 0, 0);
+        } else {
+            return new ControlCommand(0, 0, 0);  // Stop movement
+        }
+    }
+
+    public ControlCommand verticalAlign(double yOffset, double dt, Mat imgToProcess) {
+        float throttleCommand = (float) throttlePID.update(yOffset, dt, 1.0);
+        Imgproc.putText(imgToProcess, "Aligning Vertically", new Point(imgToProcess.cols() / 2.0, imgToProcess.rows() / 2.0),
+                Imgproc.FONT_HERSHEY_SIMPLEX, 1, new Scalar(0, 255, 0), 2);
+        return new ControlCommand(0, 0, throttleCommand);
+    }
+
     public ControlCommand approachLine(double dyReal, double dt, Mat imgToProcess) {
 
         if (initialDistance == 0) {

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java
new calculation to move drone (4)

@@ -343,6 +343,45 @@ public class ControllerImageDetection {
 //        return command;
 //    }
 
+    public ControlCommand approachAndLand(Mat imgToProcess) {
+        long currTime = System.currentTimeMillis();
+        double dt = (currTime - prevTime) / 1000.0;
+        prevTime = currTime;
+
+        // Step 1: Move Forward the Distance of the Blind Spot
+        double altitude = dataFromDrone.getAltitudeBelow();
+        double blindSpotDistance = calculateBlindSpotDistance(altitude);  // Based on altitude
+        ControlCommand moveForwardCommand = landingAlgorithm.moveForwardByDistance(blindSpotDistance, dt, imgToProcess);
+
+        // If still moving forward, return the command to keep moving
+        if (moveForwardCommand.getPitch() != 0 || moveForwardCommand.getRoll() != 0 || moveForwardCommand.getVerticalThrottle() != 0) {
+            return moveForwardCommand;
+        }
+
+        // Step 2: Ensure the Line is in Sight and at the Bottom of the Image
+        Point[] detectedLine = trackLine.trackSelectedLineUsingOpticalFlow(imgToProcess);
+        if (detectedLine == null) {
+            return stayOnPlace();  // Hover if no line is detected
+        }
+
+        double lineCenterY = (detectedLine[0].y + detectedLine[1].y) / 2.0;
+        if (lineCenterY < imageHeight - 20 || lineCenterY > imageHeight - 10) {
+            // Align vertically to bring the line to the desired position at the bottom
+            double yOffset = (imageHeight - 15) - lineCenterY;  // Target 10-20 pixels from bottom
+            ControlCommand alignCommand = landingAlgorithm.verticalAlign(yOffset, dt, imgToProcess);
+            return alignCommand;
+        }
+
+        // Step 3: Land
+        flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
+        return null;  // No further commands needed after landing is triggered
+    }
+
+    private double calculateBlindSpotDistance(double altitude) {
+        // Calculating blind spot distance based on altitude
+        return (altitude / 0.7) * 0.3;  // Given measurements: 0.3m blind spot per 0.7m altitude
+    }
+
     public ControlCommand alignAndLand(Mat imgToProcess) {
         long currTime = System.currentTimeMillis();
         double dt = (currTime - prevTime) / 1000.0;
@@ -438,7 +477,8 @@ public class ControllerImageDetection {
             }
 
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/LandingAlgorithm.java

@@ -26,6 +26,7 @@ public class LandingAlgorithm {
         this.throttlePID = throttlePID;
     }
 
+
     public ControlCommand moveForwardByDistance(double distance, double dt, Mat imgToProcess) {
         double currentDistance = Math.abs(distance);
         if (currentDistance > 0.05) {  // Stop when close enough (5 cm tolerance)

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java
new calculation to move drone (5)

@@ -109,6 +109,7 @@ public class ControllerImageDetection {
     private double fieldOfView = 84.0;  // Camera's horizontal field of view in degrees
     private int imageWidth = 640;  // Width of the camera feed in pixels
     private int imageHeight = 480;  // Width of the camera feed in pixels
+    private double blindSpotRatio = 0.3 / 0.7;  // 0.3 meters blind spot per 0.7 meters altitude
 
     //constructor
     public ControllerImageDetection(DataFromDrone dataFromDrone,
@@ -343,6 +344,43 @@ public class ControllerImageDetection {
 //        return command;
 //    }
 
+    public ControlCommand alignAndLand(Mat imgToProcess) {
+        long currTime = System.currentTimeMillis();
+        double dt = (currTime - prevTime) / 1000.0;
+        prevTime = currTime;
+
+        // Detect the line and get the center of the line segment
+        Point[] detectedLine = trackLine.trackSelectedLineUsingOpticalFlow(imgToProcess);
+        if (detectedLine == null) {
+            return stayOnPlace();  // Hover if no line is detected
+        }
+
+        // Calculate the distance from the line to the bottom of the image
+        double lineCenterY = (detectedLine[0].y + detectedLine[1].y) / 2.0;
+        double targetY = imageHeight - 15;  // Target position 10-20 pixels from the bottom
+        double yOffset = lineCenterY - targetY;
+
+        // Step 1: Align line to be near the bottom of the image
+        if (Math.abs(yOffset) > 5) {
+            ControlCommand alignCommand = landingAlgorithm.verticalAlign(yOffset, dt, imgToProcess);
+            return alignCommand;
+        }
+
+        // Step 2: Move forward by the blind spot distance
+        double altitude = dataFromDrone.getAltitudeBelow();
+        double blindSpotDistance = altitude * blindSpotRatio;
+        showToast("Moving forward by blind spot distance of " + blindSpotDistance + " meters.");
+        ControlCommand moveForwardCommand = landingAlgorithm.moveForwardByDistance(blindSpotDistance, dt, imgToProcess);
+
+        // Check if the command is effectively a zero movement command
+        if (moveForwardCommand.getPitch() == 0 && moveForwardCommand.getRoll() == 0 && moveForwardCommand.getVerticalThrottle() == 0) {
+            // Step 3: Land once forward movement is complete
+            flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
+        }
+
+        return moveForwardCommand;
+    }
+
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/LandingAlgorithm.java

@@ -30,7 +30,7 @@ public class LandingAlgorithm {
     public ControlCommand moveForwardByDistance(double distance, double dt, Mat imgToProcess) {
         double currentDistance = Math.abs(distance);
         if (currentDistance > 0.05) {  // Stop when close enough (5 cm tolerance)
-            float pitchCommand = (float) pitchPID.update(currentDistance, dt, 1.0);
+            float pitchCommand = (float) throttlePID.update(currentDistance, dt, 1.0);
             Imgproc.putText(imgToProcess, "Moving Forward by " + currentDistance, new Point(imgToProcess.cols() / 2.0, imgToProcess.rows() / 2.0),
                     Imgproc.FONT_HERSHEY_SIMPLEX, 1, new Scalar(0, 255, 0), 2);
             return new ControlCommand(pitchCommand, 0, 0);

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java
new calculation to move drone (6)

@@ -111,6 +111,8 @@ public class ControllerImageDetection {
     private int imageHeight = 480;  // Width of the camera feed in pixels
     private double blindSpotRatio = 0.3 / 0.7;  // 0.3 meters blind spot per 0.7 meters altitude
 
+    private int bottomTargetRangeMin = imageHeight - 20;  // Target range 10-20 pixels from bottom
+    private int bottomTargetRangeMax = imageHeight - 10;
     //constructor
     public ControllerImageDetection(DataFromDrone dataFromDrone,
                                     FlightControlMethods flightControlMethods,
@@ -344,80 +346,47 @@ public class ControllerImageDetection {
 //        return command;
 //    }
 
-    public ControlCommand alignAndLand(Mat imgToProcess) {
+    public ControlCommand executeLandingSequence(Mat imgToProcess) {
         long currTime = System.currentTimeMillis();
         double dt = (currTime - prevTime) / 1000.0;
         prevTime = currTime;
 
-        // Detect the line and get the center of the line segment
+        // Step 1: Detect the line and get the center of the line segment
         Point[] detectedLine = trackLine.trackSelectedLineUsingOpticalFlow(imgToProcess);
         if (detectedLine == null) {
             return stayOnPlace();  // Hover if no line is detected
         }
 
-        // Calculate the distance from the line to the bottom of the image
+        // Calculate vertical distance to place the line near the bottom
         double lineCenterY = (detectedLine[0].y + detectedLine[1].y) / 2.0;
-        double targetY = imageHeight - 15;  // Target position 10-20 pixels from the bottom
-        double yOffset = lineCenterY - targetY;
 
-        // Step 1: Align line to be near the bottom of the image
-        if (Math.abs(yOffset) > 5) {
-            ControlCommand alignCommand = landingAlgorithm.verticalAlign(yOffset, dt, imgToProcess);
-            return alignCommand;
-        }
-
-        // Step 2: Move forward by the blind spot distance
-        double altitude = dataFromDrone.getAltitudeBelow();
-        double blindSpotDistance = altitude * blindSpotRatio;
-        showToast("Moving forward by blind spot distance of " + blindSpotDistance + " meters.");
-        ControlCommand moveForwardCommand = landingAlgorithm.moveForwardByDistance(blindSpotDistance, dt, imgToProcess);
-
-        // Check if the command is effectively a zero movement command
[…]

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/LandingAlgorithm.java

@@ -27,10 +27,17 @@ public class LandingAlgorithm {
     }
 
 
+    public ControlCommand moveForward(double dt, Mat imgToProcess) {
+        float pitchCommand = (float) pitchPID.update(0.05, dt, 1.0);  // Example constant speed forward
+        Imgproc.putText(imgToProcess, "Moving Forward", new Point(imgToProcess.cols() / 2.0, imgToProcess.rows() / 2.0),
+                Imgproc.FONT_HERSHEY_SIMPLEX, 1, new Scalar(0, 255, 0), 2);
+        return new ControlCommand(pitchCommand, 0, 0);
+    }
+
     public ControlCommand moveForwardByDistance(double distance, double dt, Mat imgToProcess) {
         double currentDistance = Math.abs(distance);
         if (currentDistance > 0.05) {  // Stop when close enough (5 cm tolerance)
-            float pitchCommand = (float) throttlePID.update(currentDistance, dt, 1.0);
+            float pitchCommand = (float) pitchPID.update(currentDistance, dt, 1.0);
             Imgproc.putText(imgToProcess, "Moving Forward by " + currentDistance, new Point(imgToProcess.cols() / 2.0, imgToProcess.rows() / 2.0),
                     Imgproc.FONT_HERSHEY_SIMPLEX, 1, new Scalar(0, 255, 0), 2);
             return new ControlCommand(pitchCommand, 0, 0);

### 2024-10-10 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java
new calculation to move drone (7)

@@ -111,8 +111,8 @@ public class ControllerImageDetection {
     private int imageHeight = 480;  // Width of the camera feed in pixels
     private double blindSpotRatio = 0.3 / 0.7;  // 0.3 meters blind spot per 0.7 meters altitude
 
-    private int bottomTargetRangeMin = imageHeight - 20;  // Target range 10-20 pixels from bottom
-    private int bottomTargetRangeMax = imageHeight - 10;
+    private int bottomTargetRangeMin = imageHeight - 50;  // Target range 10-50 pixels from bottom
+    private int bottomTargetRangeMax = imageHeight - 20;
     //constructor
     public ControllerImageDetection(DataFromDrone dataFromDrone,
                                     FlightControlMethods flightControlMethods,

### 2024-10-20 Article/Article.tex
Continue related work and adding framework

@@
 \usepackage{xcolor}
-\usepackage{graphicx,amssymb,amsmath}
+\usepackage{graphicx,amssymb}
 \usepackage{algorithm}
@@
 \usepackage{array}
-\usepackage[utf8]{inputenc}
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
@@
 \setcounter{secnumdepth}{4}
-\usepackage{pgfplots}
 \usepackage{hyperref}
@@
 \pgfplotsset{compat=newest}
-\usepackage[utf8]{inputenc}
-\usepackage{hyperref}
-\usepackage{array}
-\usepackage{graphicx}
 %\usepackage{authblk}
@@
         \begin{keyword}
-Visual-Based Landing; Autonomous Landing; Accurate Landing; Spoken Language Recognition.
+            Visual-Based Landing \sep Autonomous Landing \sep Accurate Landing\sep Spoken Language Recognition.
         \end{keyword}
@@
     \end{figure}
+    \\
 
@@
 
-\section{Related Work} \label{sec:related}
+    \newpage \section{Related Work} \label{sec:related}
+
     \subsection{Obstacle Avoidance}
@@
 This approach effectively balances computational efficiency with the need for accurate detection and tracking, making it suitable for real-time UAV operations.
-Another approach is....
-\cite{redmon2017yolo9000}
+Another approach involves deep learning techniques like the YOLO (You Only Look Once) framework, which excels at real-time obstacle detection in dynamic environments \cite{redmon2017yolo9000}.
+YOLO9000 enables rapid detection of multiple objects, making it ideal for fast decision-making in complex surroundings.
+Its efficiency and accuracy have made it a popular choice for enhancing UAV obstacle avoidance systems.
 
+    \subsection{Motion Detection and Object Detection: Yolo (You Only Look Once)}
+    Recent advancements in motion and object detection have been significantly influenced by the YOLO (You Only Look Once) framework.
+As highlighted by \cite{dahirou2021motion}, YOLO enables real-time object detection by predicting bounding boxes and class probabilities from full images in a single evaluation, enhancing both speed and accuracy.
+This capability makes YOLO particularly effective for applications requiring immediate responsiveness, such as surveillance and autonomous navigation.
+
+    \subsection{Speech Recognition}
+    Speech recognition has been explored as a key component in enhancing drone operation through voice commands, particularly in environments where manual control is impractical.
+Various systems have been developed for continuous speech recognition on Android devices, such as the one proposed by Srivastav et al.
+\cite{SpeechRecognition}, which enables real-time voice command processing for mobile platforms.
+This technology is critical for integrating human-drone interaction, especially in hands-free scenarios, allowing operators to issue commands without physical intervention.
+Such advancements enable drones to act upon voice inputs for tasks like navigation, object detection, or activation of specific modes.
+Similar systems have been implemented to facilitate the control of unmanned aerial vehicles (UAVs) in real-time, optimizing human-machine interaction and expanding the use cases for drones in dynamic, complex environments.
+
+    \subsection{A Robust and Accurate Landing Methodology for Drones on Moving Targets}
+    Recent work has explored the use of ArUco markers for precision landing in autonomous drones, offering an efficient visual processing solution for target detection and tracking.
+As demonstrated in \cite{drones6040098}, ArUco markers provide high accuracy in identifying landing zones, especially when combined with robust visual algorithms.
+This approach addresses common challenges such as variable lighting conditions and drone stability during descent.
+Implementing these markers has shown success in enhancing landing precision, contributing to safer and more reliable autonomous operations.
+
+    \subsection{An improved Canny edge detection algorithm}
+    Edge detection algorithms play a critical role in enhancing the visual processing capabilities of drones by accurately identifying boundaries and objects within an image.
+The Canny Edge Detection Algorithm, as discussed in \cite{rong2014improved}, has proven to be highly effective due to its ability to detect edges with minimal noise while maintaining high accuracy.
+This method ensures that drones can detect and track obstacles, aiding in precise navigation and autonomous landing.
+Its application in real-time drone systems highlights its importance in improving the robustness of visual navigation and obstacle avoidance.
 % \cite{lee2022camera} is a set.
@@
 
-\section{Datasets} \label{sec:datasets}
+% \section{Datasets} \label{sec:datasets}
 
-In the field of speech recognition, the ability to accurately transcribe
+% In the field of speech recognition, the ability to accurately transcribe
+
+    \section{Drone Control Mechanisms} \label{sec:framework}
+    The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle.
+These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.\\
+    \begin{description}
+        \item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
+        \item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
+        \item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
+        \item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
+    \end{description}
+    //Maybe add more? about the remote also?
 
     \section{Framework} \label{sec:framework}
+    \subsection{Speech Recognition}
+    The speech recognition system continuously listens for voice commands, enabling real-time control of the drone without touching the screen. \\
+    Each recognized command triggers a specific action in the drone. The key commands and their associated actions are:
+    \begin{description}
+        \item $\bullet$ Takeoff - Initiates the drone's takeoff sequence, lifting it to a designated altitude for hover.
+        \item $\bullet$ Land - Initiates the landing sequence, lowering the throttle for a controlled descent until the drone reaches the ground.
+        \item $\bullet$ Stop - Halts any current movement, keeping the drone stationary in hover mode.
+        \item $\bullet$ Move up - Increases the throttle to elevate the drone vertically.
+        \item $\bullet$ Move down - Decreases the throttle, causing the drone to descend.
+        \item $\bullet$ Start recording - Begins video recording using the drone's camera.
+        \item $\bullet$ Stop recording - Stops the video recording and saves the footage.
+        \item $\bullet$ Edge detection - Activates the edge detection algorithm, allowing the system to identify and process edges for navigation or object tracking.
+
+    \end{description}
+    \subsection{Object Tracking?}
+    \subsection{Landing Algorithm}
+    \subsection{Movement Detection}
 

### 2024-10-21 Article/Article.tex
Add Algorithm design and Future work sections

@@
 
-        \author[a]{Adi Peisach}
-        \ead{adi.peisach@gmail.com}
+% \author[a]{Adi Peisach}
+% \ead{adi.peisach@gmail.com}
 
@@
 For precise landings at the edge of a rooftop, an edge detection algorithm is employed alongside a target line selection process, allowing the user to designate a specific landing line beforehand, ensuring accuracy during the final approach.
-
 \end{abstract}
@@
 Our approach is tested on a DJI drone equipped with a standard camera, using the DJI SDK for implementation on Android devices.
-Additionally, we have implemented a "guard" mode in the app—a button that, when activated, is designed to detect movement (such as people, cars, etc.) and send alerts.
-The system's robustness is further enhanced by incorporating basic voice commands through a speech recognition module, meeting the requirements outlined by MAFAT.
+Additionally, we have implemented a "guard" mode in the app — a button that, when activated, is designed to detect movement (such as people, cars, etc.) and send alerts.
+The system's robustness is further enhanced by incorporating basic voice commands through a speech recognition module, meeting the requirements outlined by MAFAT.\\
 
-    \begin{figure}[htp]
+\newpage \section{Algorithm Design} \label{sec:algorithm}
+Our proposed algorithm for autonomous drone landing consists of three key components: Target Line Selection, Flight Control, and Object Detection.
+Each part contributes to the overall reliability and precision of the landing process, ensuring safe navigation and obstacle avoidance.
+
+\begin{figure}[H]
     \centering
-        \includegraphics[width=11.0cm]{Schematic_for_automatic_landing.png}
+    \includegraphics[width=0.7\textwidth]{Schematic_for_automatic_landing.png}  % Reduced the size here
     \caption{Schematic for automatic landing.}
@@
 \end{figure}
-    \\
 
-% \subsection{Paper Structure}
-% This paper is structured as follows: Section \ref{sec:related} discusses related work in autonomous drone landing and visual navigation.
-Section \ref{sec:datasets} details the datasets used for testing and validation.
-Section \ref{sec:framework} describes the proposed framework, including the algorithms and implementation details.
-Section \ref{sec:exp_eval} presents the experimental evaluation and results.
-Finally, Section \ref{sec:discussion} offers a discussion on the findings, and Section \ref{sec:conclusions} concludes the paper with suggestions for future work.
+\subsection{Target Line Selection}
+In the first stage of the landing process, edge detection is activated to identify all available and compatible lines within the camera's field of view.
+These lines represent potential landing paths.
+The user interacts with the system by selecting the desired line for the drone to land behind via a touch-based interface.
+Once the target line is chosen, the algorithm continuously tracks the line.
+This is achieved by calculating the distance between the selected line and all detected lines, and the one with the minimum distance is updated as the current target line.
+This real-time tracking ensures that the drone can maintain accurate navigation towards the desired landing area.
 
-% \begin{table}[th]
-%   \caption{List of abbreviations}
+\subsection{Flight Control}
+After target line selection, the system activates the flight control module.
+The drone begins moving towards the selected line by issuing pitch commands, which direct forward movement.
+This continues until the chosen line is nearly out of the drone’s visible range.
+Through experimental measurements, we identified a blind spot between the drone's final visible position of the line and its actual location in reality.
+To compensate for this, the algorithm calculates the necessary adjustment and issues a final pitch command, ensuring that the drone reaches the correct position relative to the target line.
 
-%   \centering
-%   \begin{tabular}{ |c|c|c|}
-%   \hline
-%     \multicolumn{1}{|c|}{\textbf{Abbreviation}} &
-%     \multicolumn{1}{|c|}{\textbf{Meaning}}\\\hline
-%     PID & \quad Proportional Integral Derivative \\\hline
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.7\textwidth]{Blind Spot Area.png}  % Reduced the size here
+    % \caption{Schematic for automatic landing.}
+    \label{fig:Blind Spot Area.}
+\end{figure}
 
-%   \end{tabular}
-%   \label{tab:list_of_abbreviations}
-% \end{table}
+\subsection{Object Detection}
+Upon reaching the target area, object detection is initiated to scan for potential hazards in the intended landing zone.
+The detection algorithm examines the area for obstacles such as people, vehicles, or other objects that may hinder safe landing.
+The landing zone's dimensions are calculated based on prior measurements from different drone positions, ensuring the detection area is appropriately scaled for accurate hazard identification.
+If no hazards are detected, the system proceeds with the landing sequence, ensuring a safe and precise touchdown.
 
@@
 Its application in real-time drone systems highlights its importance in improving the robustness of visual navigation and obstacle avoidance.
-% \cite{lee2022camera} is a set.
-
-% Spoken language recognition (SLR) has been a
-
-% \section{Datasets} \label{sec:datasets}
-
-% In the field of speech recognition, the ability to accurately transcribe
 
@@
 \end{description}
-    //Maybe add more? about the remote also?
 
@@
 \subsection{Speech Recognition}
-    The speech recognition system continuously listens for voice commands, enabling real-time control of the drone without touching the screen. \\
+The speech recognition system, powered by Google Speech Recognition, continuously listens for the user’s voice until it detects the wake word "hey rexi." Once activated, the system checks subsequent speech for commands from the predefined list, enabling real-time control of the drone without touching the screen.
+This approach allows the system to remain responsive while minimizing unnecessary processing, facilitating a hands-free operation experience.
+
 Each recognized command triggers a specific action in the drone. The key commands and their associated actions are:
@@
 
-    \section{Experimental Evaluation and Results} \label{sec:exp_eval}
-
-    In accordance with the methodologies outlined in the framework, several modifications were independently evaluated.
-Below is a tabulated comparison illustrating the differences among these variations, as in Table~\ref{tab:results_comparison}:
-
-    \begin{table}[ht]
-        \centering
-        \caption{Comparative Analysis of Model Improvements on Validation Dataset.}
-        \label{tab:results_comparison}
-        \resizebox{0.4\textwidth}{!}{%
-            \begin{tabular}{|c|c|}
-                \hline
-                \textbf{Model} & \textbf{Accuracy} \\
-                \hline
-                Baseline & 0.54 \\
-
-                \hline
-            \end{tabular}%
-        }
-    \end{table}
-
-    Figure~\ref{fig:conf_matrix_test} depicting the confusion matrices for the final model on :
-
-    \begin{figure}[htp]
-        \centering
-        \includegraphics[width=11.0cm]{con_matrix_test.jpeg}
-        \caption{Confusion Matrix on Validation Dataset for the Final Model, showing minimal error.}
-        \label{fig:conf_matrix_test}
-    \end{figure}
-
-    The results in Eq.(\ref{eq:inequality}) clearly demonstrate that Boaz has no idea in equations.
-
-    \begin{equation} \label{eq:inequality}
-    3 \neq 3
-    \end{equation}
-
 \section{Discussion} \label{sec:discussion}
@@
 
-    \section{Conclusions and Future Work} \label{sec:conclusions}
+\newpage \section{Future Work} \label{sec:future}
+An important area for future improvement is the algorithm's ability to handle wind conditions, particularly in outdoor environments and at higher altitudes.
+While the current implementation performs reliably in controlled settings, real-world scenarios—such as fluctuating wind speeds and changing directions—pose significant challenges to the drone's stability and landing accuracy.
+Specifically, turbulence at great heights can disrupt the drone's trajectory, leading to deviations from the intended flight path and reducing the precision of both target line tracking and landing position.
 
-    In this study, we have
+To address these challenges, we plan to enhance the algorithm by integrating real-time wind compensation techniques.
+This improvement will involve adapting the flight control module to account for external forces, using sensor and visual data to counteract wind disturbances, and dynamically adjusting the drone's movements.
+Enhancing wind handling will enable the algorithm to perform more reliably across a wider range of scenarios, ensuring consistent operation in varying environmental conditions.
+
+Additional future work includes transitioning the speech recognition system from an online to an offline model, which will improve reliability by ensuring consistent functionality without internet access.
+Furthermore, we plan to explore the integration of plane recognition algorithms to enhance landing precision.
+This capability will enable the drone to autonomously identify suitable landing surfaces, thus increasing safety and operational efficiency.
+
+\section{Conclusion}
 

### 2024-10-21 Article/Article.tex
Add Conclusion section

@@
 \section{Conclusion}
+In this work, we presented a novel approach for autonomous drone landing using a visual-based framework that eliminates the need for GPS.
+Our algorithm, tested on a DJI drone equipped with a standard camera, successfully integrates object detection, edge detection, and flight control to enable precise landings.
+The system's performance in controlled environments demonstrates its effectiveness, especially in scenarios where GPS signals are unreliable or unavailable.\\
+
+However, there are still challenges to address, particularly in handling unpredictable wind conditions and ensuring the system’s reliability in diverse outdoor environments.
+Future work will focus on improving the algorithm’s robustness in real-world scenarios and enhancing its functionality through additional features such as offline speech recognition and plane recognition algorithms for safer and more autonomous landings.\\
+
+The combination of these developments will pave the way for safer, more reliable, and efficient drone operations in a wide variety of applications, from urban package delivery to military surveillance missions.
 

### 2024-10-21 Article/Article.tex
Add Movement Detection section

@@
 
+\section{Related Work} \label{sec:related}
+\subsection{Obstacle Avoidance}
+Obstacle avoidance is a critical aspect of autonomous drone operations, especially in dynamic environments where both static and moving obstacles are present.
+One approach is integrating depth images with an occupancy voxel map to detect and track dynamic obstacles \cite{xu2023real}.
+This approach effectively balances computational efficiency with the need for accurate detection and tracking, making it suitable for real-time UAV operations.
+Another approach involves deep learning techniques like the YOLO (You Only Look Once) framework, which excels at real-time obstacle detection in dynamic environments \cite{redmon2017yolo9000}.
+YOLO9000 enables rapid detection of multiple objects, making it ideal for fast decision-making in complex surroundings.
+Its efficiency and accuracy have made it a popular choice for enhancing UAV obstacle avoidance systems.
+
+\subsection{Motion Detection and Object Detection: Yolo (You Only Look Once)}
+Recent advancements in motion and object detection have been significantly influenced by the YOLO (You Only Look Once) framework.
+As highlighted by \cite{dahirou2021motion}, YOLO enables real-time object detection by predicting bounding boxes and class probabilities from full images in a single evaluation, enhancing both speed and accuracy.
+This capability makes YOLO particularly effective for applications requiring immediate responsiveness, such as surveillance and autonomous navigation.
+
+\subsection{Speech Recognition}
+Speech recognition has been explored as a key component in enhancing drone operation through voice commands, particularly in environments where manual control is impractical.
+Various systems have been developed for continuous speech recognition on Android devices, such as the one proposed by Srivastav et al.
+\cite{SpeechRecognition}, which enables real-time voice command processing for mobile platforms.
+This technology is critical for integrating human-drone interaction, especially in hands-free scenarios, allowing operators to issue commands without physical intervention.
+Such advancements enable drones to act upon voice inputs for tasks like navigation, object detection, or activation of specific modes.
+Similar systems have been implemented to facilitate the control of unmanned aerial vehicles (UAVs) in real-time, optimizing human-machine interaction and expanding the use cases for drones in dynamic, complex environments.
+
+\subsection{A Robust and Accurate Landing Methodology for Drones on Moving Targets}
+Recent work has explored the use of ArUco markers for precision landing in autonomous drones, offering an efficient visual processing solution for target detection and tracking.
+As demonstrated in \cite{drones6040098}, ArUco markers provide high accuracy in identifying landing zones, especially when combined with robust visual algorithms.
+This approach addresses common challenges such as variable lighting conditions and drone stability during descent.
+Implementing these markers has shown success in enhancing landing precision, contributing to safer and more reliable autonomous operations.
+
+\subsection{An improved Canny edge detection algorithm}
+Edge detection algorithms play a critical role in enhancing the visual processing capabilities of drones by accurately identifying boundaries and objects within an image.
+The Canny Edge Detection Algorithm, as discussed in \cite{rong2014improved}, has proven to be highly effective due to its ability to detect edges with minimal noise while maintaining high accuracy.
+This method ensures that drones can detect and track obstacles, aiding in precise navigation and autonomous landing.
+Its application in real-time drone systems highlights its importance in improving the robustness of visual navigation and obstacle avoidance.
+
+\section{Drone Control Mechanisms} \label{sec:mechanisms}
+The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle.
+These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.\\
+\begin{description}
+\item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
+\item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
+\item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
+\item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
+\end{description}
+
 \newpage \section{Algorithm Design} \label{sec:algorithm}
@@
 
-\newpage \section{Related Work} \label{sec:related}
+\section{Movement Detection}
+An important aspect of this project is the integration of movement detection, designed to enhance the drone’s functionality as a surveillance tool.
+Once the drone has landed on a designated edge, it operates as a stationary surveillance camera.
+In this mode, the system continuously monitors the surrounding environment for movement.\\
 
-\subsection{Obstacle Avoidance}
-Obstacle avoidance is a critical aspect of autonomous drone operations, especially in dynamic environments where both static and moving obstacles are present.
-One approach is integrating depth images with an occupancy voxel map to detect and track dynamic obstacles \cite{xu2023real}.
-This approach effectively balances computational efficiency with the need for accurate detection and tracking, making it suitable for real-time UAV operations.
-Another approach involves deep learning techniques like the YOLO (You Only Look Once) framework, which excels at real-time obstacle detection in dynamic environments \cite{redmon2017yolo9000}.
-YOLO9000 enables rapid detection of multiple objects, making it ideal for fast decision-making in complex surroundings.
-Its efficiency and accuracy have made it a popular choice for enhancing UAV obstacle avoidance systems.
+Movement detection is implemented using the YOLO (You Only Look Once) object detection framework, which enables real-time identification of objects such as people, vehicles, or other moving entities.
+When movement is detected, the system immediately alerts the user through the app.
+This alert includes both a voice notification, specifying what has been detected, and a text message displayed on the screen.
+These alerts provide real-time updates, enabling timely responses to any potential security concerns.
 
-\subsection{Motion Detection and Object Detection: Yolo (You Only Look Once)}
-Recent advancements in motion and object detection have been significantly influenced by the YOLO (You Only Look Once) framework.
-As highlighted by \cite{dahirou2021motion}, YOLO enables real-time object detection by predicting bounding boxes and class probabilities from full images in a single evaluation, enhancing both speed and accuracy.
-This capability makes YOLO particularly effective for applications requiring immediate responsiveness, such as surveillance and autonomous navigation.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.7\textwidth]{movementDetect.jpeg}  % Reduced the size here
+    % \caption{Guardian mode activated.}
+    \label{fig:movementDetect.}
+\end{figure}
 
-\subsection{Speech Recognition}
-Speech recognition has been explored as a key component in enhancing drone operation through voice commands, particularly in environments where manual control is impractical.
-Various systems have been developed for continuous speech recognition on Android devices, such as the one proposed by Srivastav et al.
-\cite{SpeechRecognition}, which enables real-time voice command processing for mobile platforms.
-This technology is critical for integrating human-drone interaction, especially in hands-free scenarios, allowing operators to issue commands without physical intervention.
-Such advancements enable drones to act upon voice inputs for tasks like navigation, object detection, or activation of specific modes.
-Similar systems have been implemented to facilitate the control of unmanned aerial vehicles (UAVs) in real-time, optimizing human-machine interaction and expanding the use cases for drones in dynamic, complex environments.
-
-\subsection{A Robust and Accurate Landing Methodology for Drones on Moving Targets}
-Recent work has explored the use of ArUco markers for precision landing in autonomous drones, offering an efficient visual processing solution for target detection and tracking.
-As demonstrated in \cite{drones6040098}, ArUco markers provide high accuracy in identifying landing zones, especially when combined with robust visual algorithms.
-This approach addresses common challenges such as variable lighting conditions and drone stability during descent.
-Implementing these markers has shown success in enhancing landing precision, contributing to safer and more reliable autonomous operations.
-
-\subsection{An improved Canny edge detection algorithm}
-Edge detection algorithms play a critical role in enhancing the visual processing capabilities of drones by accurately identifying boundaries and objects within an image.
-The Canny Edge Detection Algorithm, as discussed in \cite{rong2014improved}, has proven to be highly effective due to its ability to detect edges with minimal noise while maintaining high accuracy.
-This method ensures that drones can detect and track obstacles, aiding in precise navigation and autonomous landing.
-Its application in real-time drone systems highlights its importance in improving the robustness of visual navigation and obstacle avoidance.
-
-\section{Drone Control Mechanisms} \label{sec:framework}
-The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle.
-These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.\\
-\begin{description}
-\item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
-\item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
-\item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
-\item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
-\end{description}
-
-\section{Framework} \label{sec:framework}
-\subsection{Speech Recognition}
+\section{Speech Recognition} \label{sec:SpeechRecognition}
 The speech recognition system, powered by Google Speech Recognition, continuously listens for the user’s voice until it detects the wake word "hey rexi." Once activated, the system checks subsequent speech for commands from the predefined list, enabling real-time control of the drone without touching the screen.
@@
 \end{description}
-\subsection{Object Tracking?}
-\subsection{Landing Algorithm}
-\subsection{Movement Detection}
 
-\section{Discussion} \label{sec:discussion}
+% \section{Discussion} \label{sec:discussion}
 
-Advancements in language recognition technologies have been noteworthy, yet they confront several challenges and limitations. This discussion highlights some of the prevalent issues:
+% Advancements in language recognition technologies have been noteworthy, yet they confront several challenges and limitations. This discussion highlights some of the prevalent issues:
 
-\begin{enumerate}
+% \begin{enumerate}
 
-    \item \textbf{Linguistic Ambiguity.} Distinguishing between languages with shared linguistic traits
+%     \item \textbf{Linguistic Ambiguity.} Distinguishing between languages with shared linguistic traits
 
-    \item \textbf{Code-Switching Phenomenon.} In multilingual settings,
+%     \item \textbf{Code-Switching Phenomenon.} In multilingual settings,
 
-\end{enumerate}
+% \end{enumerate}
 

### 2024-10-22 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ALRemoteControllerView.java
Deleting unused files + unused functions + fixing readme

@@ -9,7 +9,6 @@ import android.graphics.Bitmap;
 import android.graphics.Color;
 import android.graphics.SurfaceTexture;
 import android.graphics.drawable.BitmapDrawable;
-import android.media.AudioManager;
 import android.os.Handler;
 import android.speech.tts.TextToSpeech;
 import android.util.Log;
@@ -38,7 +37,6 @@ import org.opencv.core.Point;
 import java.util.Arrays;
 import java.util.Locale;
 
-import dji.common.model.LocationCoordinate2D;
 import dji.sdk.codec.DJICodecManager;
 
 
@@ -90,7 +88,6 @@ public class ALRemoteControllerView extends RelativeLayout
     private float pitch = 0.2f, yaw = 0.5f, roll = 0.2f, throttle = 0.2f; //0.2f;
     // depthmap.py video display
     private ImageView imageView;
-    private boolean videoNotStarted = true;
     private YoloDetector yoloDetector;
     private boolean isMovementDetectionRunning = false;
     private Handler movementDetectionHandler = new Handler();
@@ -125,7 +122,6 @@ public class ALRemoteControllerView extends RelativeLayout
         initYoloDetector(context);
 
         accuracyLog = new AccuracyLog(dataLog, dist, this.getContext());
-//        accuracyLog = new AccuracyLog(dist, this.getContext());
 
         dataFromDrone = new DataFromDrone();
         flightCommands = new FlightCommands();
@@ -167,14 +163,6 @@ public class ALRemoteControllerView extends RelativeLayout
                 Log.e("TTS", "TextToSpeech initialization failed");
             }
         });
-//        AudioManager audioManager = (AudioManager) context.getSystemService(Context.AUDIO_SERVICE);
-//        AudioManager.OnAudioFocusChangeListener focusChangeListener = focusChange -> {
-//            if (focusChange == AudioManager.AUDIOFOCUS_LOSS) {
-//                // Handle audio focus loss
-//            }
-//        };
-//        audioManager.requestAudioFocus(focusChangeListener, AudioManager.STREAM_MUSIC, AudioManager.AUDIOFOCUS_GAIN_TRANSIENT);
-
     }
 
     @Override
@@ -242,24 +230,13 @@ public class ALRemoteControllerView extends RelativeLayout
                 return true;
             });
         }
-//        goToFMM_btn = findViewById(R.id.GoTo_FMM_btn);
[…]

### 2024-10-22 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/CenterTracker.java

@@ -1,196 +1,0 @@
-package com.dji.sdk.sample.demo.accurateLandingController;
-
-import org.opencv.core.Mat;
-import org.opencv.core.Point;
-import org.opencv.core.Rect;
-import org.opencv.core.Rect2d;
-import org.opencv.core.Scalar;
-import org.opencv.imgproc.Imgproc;
-import org.opencv.tracking.TrackerCSRT;
-import org.opencv.tracking.TrackerKCF;
-import org.opencv.tracking.Tracking;
-
-import org.opencv.video.Tracker;
-
-public class CenterTracker {
-    private static final double PITCH_SCALING_FACTOR = 0.01;
-    private static final double ROLL_SCALING_FACTOR = 0.01;
-    private boolean gotFirstImage;
-    private Rect currentRect;
-    private Drawing mDrawing = Drawing.DRAWING;
-    private boolean isPaused;
-    private String alg = "TrackerKCF";
-    private double initialLatitude;
-    private double initialLongitude;
-    private int size;
-    protected Tracker mTracker;
-    private Mat mImageGrab;
-
-    public CenterTracker(int size, String alg) {
-        this.size = size;
-        this.alg = alg;
-    }
-
-
-    public CenterTracker() {
-        size = 50;
-        alg = "TrackerKCF";
-    }
-
-    public Mat init(Mat frame) {
-
-//        switch (alg) {
-//            case "TrackerCSRT":
-//                mTracker = TrackerCSRT.create();
-//                break;
-//            case "TrackerKCF":
-//                mTracker = TrackerKCF.create();
-//                break;
-//        }
-        mTracker = (Tracker) TrackerKCF.create();
-
-        currentRect = selectROI(frame);
-
-        mTracker.init(frame, currentRect);
-//        currentRect = mInitRectangle;
-
-        Tracking t = new Tracking();
-
-//        mDrawing = Drawing.TRACKING;
-//
-//        //TODO: DEBUG
-//        Rect testRect = new org.opencv.core.Rect(currentRect.x, currentRect.y, currentRect.width, currentRect.height);
-//        Mat roi = new Mat(mImageGrab, testRect);
-//        Bitmap bmp = null;
-//        Mat tmp = new Mat (roi.rows(), roi.cols(), CvType.CV_8U, new Scalar(4));
-//        try {
-//            Imgproc.cvtColor(roi, tmp, Imgproc.COLOR_RGB2BGRA);
[…]

### 2024-10-22 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java

@@ -5,75 +5,42 @@ import static org.opencv.android.Utils.matToBitmap;
 
 import android.content.Context;
 import android.graphics.Bitmap;
-import android.graphics.BitmapFactory;
 import android.graphics.Color;
-import android.os.Handler;
-import android.os.Looper;
-import android.util.Base64;
 import android.util.Log;
 import android.widget.Button;
 import android.widget.ImageView;
 
 import androidx.annotation.Nullable;
 
-import com.chaquo.python.PyObject;
-import com.chaquo.python.Python;
-import com.chaquo.python.android.AndroidPlatform;
 import com.dji.sdk.sample.demo.kcgremotecontroller.VLD_PID;
 import com.dji.sdk.sample.internal.controller.DJISampleApplication;
 
 import org.opencv.android.Utils;
 import org.opencv.core.Mat;
-import org.opencv.core.MatOfByte;
 import org.opencv.core.Point;
 import org.opencv.core.Scalar;
-import org.opencv.imgcodecs.Imgcodecs;
 import org.opencv.imgproc.Imgproc;
 
-import java.util.ArrayList;
 import java.util.Arrays;
 import java.util.HashMap;
 import java.util.List;
 import java.util.Map;
 import java.util.Objects;
-import java.util.concurrent.ExecutorService;
-import java.util.concurrent.Executors;
 
 public class ControllerImageDetection {
 
     // depth map python view
 
     private static final String TAG = ControllerImageDetection.class.getSimpleName();
-    private static final double MAX_VELOCITY = 0.5; // Maximum velocity in m/s
-    private static final double DEADBAND = 0.05; // Deadband in meters
-    private final int displayFps = 0;
     private final DataFromDrone dataFromDrone;
-    private final int DISTANCE_HISTORY_SIZE = 3; // Reduced history size for quicker response
-    private final int CONSISTENT_FRAMES_REQUIRED = 5;
-    //    Double PP = 0.5, II = 0.02, DD = 0.01, MAX_I = 0.5;
     Double PP = 0.05, II = 0.02, DD = 0.01, MAX_I = 0.5;
     private ImageView imageView;  // ImageView to display the frames
-    private boolean isPlaying = false;  // To control the video playback
-    private boolean isDetectingPlane = false;
-    private int landingMode = 0;
     private boolean isObjectDetecting = false;
-    private Handler handler = new Handler(Looper.getMainLooper());  // For updating the UI
-    private Python python;
-    private double focal_length = 4.8; // Field of View in mm
[…]

### 2024-10-22 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/DericheEdgeDetection.java

@@ -1,71 +1,0 @@
-package com.dji.sdk.sample.demo.accurateLandingController;
-
-import org.opencv.core.Core;
-import org.opencv.core.Mat;
-
-public class DericheEdgeDetection {
-
-    private static final double ALPHA = 1.0; // Example alpha value
-
-    // Recursive Deriche filter in horizontal direction
-    private static Mat applyHorizontalDeriche(Mat input, double alpha) {
-        Mat output = Mat.zeros(input.size(), input.type());
-        int rows = input.rows();
-        int cols = input.cols();
-
-        for (int i = 0; i < rows; i++) {
-            double[] previous = input.get(i, 0);
-            double[] current = new double[cols];
-
-            for (int j = 0; j < cols; j++) {
-                if (j == 0) {
-                    current[j] = previous[0];
-                } else {
-                    double[] prevValue = input.get(i, j - 1);
-                    current[j] = alpha * prevValue[0] + (1 - alpha) * previous[j];
-                }
-            }
-            output.put(i, 0, current);
-        }
-        return output;
-    }
-
-    // Recursive Deriche filter in vertical direction
-    private static Mat applyVerticalDeriche(Mat input, double alpha) {
-        Mat output = Mat.zeros(input.size(), input.type());
-        int rows = input.rows();
-        int cols = input.cols();
-
-        for (int j = 0; j < cols; j++) {
-            double[] previous = input.get(0, j);
-            double[] current = new double[rows];
-
-            for (int i = 0; i < rows; i++) {
-                if (i == 0) {
-                    current[i] = previous[0];
-                } else {
-                    double[] prevValue = input.get(i - 1, j);
-                    current[i] = alpha * prevValue[0] + (1 - alpha) * previous[i];
-                }
-            }
-            output.put(0, j, current);
-        }
-        return output;
-    }
-
-    // Full Deriche edge detection process
-    public static Mat detectEdges(Mat input, double alpha) {
-        // Step 1: Apply Deriche filter in horizontal direction
-        Mat horizontalFiltered = applyHorizontalDeriche(input, alpha);
-
-        // Step 2: Apply Deriche filter in vertical direction
-        Mat verticalFiltered = applyVerticalDeriche(horizontalFiltered, alpha);
-
-        // Step 3: Compute Gradient Magnitude (hypot function)
-        Mat gradientMagnitude = new Mat();
-        Core.magnitude(horizontalFiltered, verticalFiltered, gradientMagnitude);
-
[…]

### 2024-10-22 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/GimbalController.java

@@ -1,13 +1,10 @@
 package com.dji.sdk.sample.demo.accurateLandingController;
 
-import com.dji.sdk.sample.demo.kcgremotecontroller.Controller;
 import com.dji.sdk.sample.demo.kcgremotecontroller.gimbelListener;
 import com.dji.sdk.sample.internal.utils.CallbackHandlers;
 import com.dji.sdk.sample.internal.utils.ModuleVerificationUtil;
 import com.dji.sdk.sample.internal.utils.ToastUtils;
 
-import java.util.LinkedList;
-import java.util.List;
 import java.util.concurrent.atomic.AtomicBoolean;
 
 import dji.common.flightcontroller.virtualstick.FlightCoordinateSystem;
@@ -30,9 +27,7 @@ public class GimbalController implements gimbelListener {
     FlightController flightController;
     boolean finishRotate = false;
     private float gimbalValue = 0;
-    private Controller controller;
     private Gimbal gimbal = null;
-    private List<gimbelListener> gimbelListenersList = new LinkedList<gimbelListener>();
     private float prevDegree = -1000;
     private int maxGimbalDegree = 1000;
     private int minGimbalDegree = -1000;

### 2024-10-22 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/LandingAlgorithm.java

@@ -37,34 +37,6 @@ public class LandingAlgorithm {
         return new ControlCommand(pitchCommand, 0, 0);
     }
 
-//    public ControlCommand moveForwardByDistance(double targetDistance, double dt, Mat imgToProcess) {
-//        // Calculate remaining distance to target
-//        double remainingDistance = targetDistance - cumulativeDistance;
-//
-//        // Stop if we’re within the 3 cm tolerance
-//        if (remainingDistance <= 0.03) {
-//            // Reset cumulative distance for next movement
-//            cumulativeDistance = 0;
-//            Imgproc.putText(imgToProcess, "(3) Stopping", new Point(imgToProcess.cols() / 2.0, imgToProcess.rows() / 2.0),
-//                    Imgproc.FONT_HERSHEY_SIMPLEX, 1, new Scalar(0, 255, 0), 2);
-//            return new ControlCommand(0, 0, 0);
-//        }
-//
-//        // Calculate adjusted velocity based on remaining distance
-//        float adjustedVelocity = (float) Math.min(remainingDistance / 2.0, maxVelocity);
-//
-//        // Update pitch command using PID
-//        float pitchCommand = (float) pitchPID.update(adjustedVelocity, dt, maxVelocity);
-//
-//        // Calculate the distance traveled this cycle and update cumulative distance
-//        double distanceTraveledThisCycle = adjustedVelocity * dt;
-//        cumulativeDistance += distanceTraveledThisCycle;
-//
-//        Imgproc.putText(imgToProcess, "(2) Moving Forward by " + remainingDistance, new Point(imgToProcess.cols() / 2.0, imgToProcess.rows() / 2.0),
-//                Imgproc.FONT_HERSHEY_SIMPLEX, 1, new Scalar(0, 255, 0), 2);
-//        return new ControlCommand(pitchCommand, 0, 0);
-//    }
-
     public ControlCommand moveForwardByDistance(double distance, double dt, Mat imgToProcess) {
 
         // Decelerate as we approach the target
@@ -117,9 +89,5 @@ public class LandingAlgorithm {
             initialDistance = 0;  // Reset for next movement
             return new ControlCommand(0, 0, 0);  // Stop movement
         }
-    }
-
-    public void resetDistance() {
-        initialDistance = 0;
     }
 }

### 2024-10-22 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ReadFromKmlFile.java

@@ -1,109 +1,0 @@
-package com.dji.sdk.sample.demo.accurateLandingController;
-
-import android.content.Context;
-import android.content.res.Resources;
-import android.util.Xml;
-
-import com.dji.sdk.sample.R;
-
-import org.xmlpull.v1.XmlPullParser;
-import org.xmlpull.v1.XmlPullParserException;
-import org.xmlpull.v1.XmlPullParserFactory;
-
-import java.io.BufferedReader;
-import java.io.IOException;
-import java.io.InputStream;
-import java.io.InputStreamReader;
-import java.util.HashMap;
-import java.util.Map;
-
-public class ReadFromKmlFile {
-    private final Map<String, GPSLocation> coordinatesMap;
-    private final Context context;
-
-    public ReadFromKmlFile(Context context) {
-        coordinatesMap = new HashMap<>();
-        this.context = context;
-        readKml();
-        print();
-    }
-
-    public void print(){
-        for (HashMap.Entry<String, GPSLocation> entry : coordinatesMap.entrySet()) {
-            String name = entry.getKey();
-            GPSLocation coordinate = entry.getValue();
-
-            double latitude = coordinate.getLatitude();
-            double longitude = coordinate.getLongitude();
-            double altitude = coordinate.getAltitude();
-
-            System.out.println("Name: " + name);
-            System.out.println("Latitude: " + latitude);
-            System.out.println("Longitude: " + longitude);
-            System.out.println("Altitude: " + altitude);
-            System.out.println("-------------------");
-        }
-    }
-
-    public void readKml() {
-
-        Resources resources = context.getResources();
-        try {
-            // Open the InputStream for the KML file
-            InputStream inputStream = resources.openRawResource(R.raw.university_places); // Replace with your KML file name
-
-            XmlPullParserFactory factory = XmlPullParserFactory.newInstance();
-            factory.setNamespaceAware(true);
-            XmlPullParser parser = factory.newPullParser();
-            parser.setInput(inputStream, null);
-
-            int eventType = parser.getEventType();
-            String currentTag = "";
-            String currentName = "";
-            double currentLatitude = 0;
-            double currentLongitude = 0;
-            double currentAltitude = 0;
-
-            while (eventType != XmlPullParser.END_DOCUMENT) {
-                switch (eventType) {
-                    case XmlPullParser.START_TAG:
-                        currentTag = parser.getName();
-                        break;
-                    case XmlPullParser.TEXT:
[…]

### 2024-10-23 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ALRemoteControllerView.java
Add gimbal rotation for guard mode. Clean some code.

@@ -496,13 +496,7 @@ public class ALRemoteControllerView extends RelativeLayout
             case R.id.EdgeDetect:
                 accurateLanding();
                 break;
-//            case R.id.Follow_phone_FMM_btn:
-//                followPhone();
-//                break;
 
-//            case R.id.GoTo_FMM_btn:
-//                this.goToFMM_BTN();
-//                break;
             case R.id.stop_btn:
                 stopBtnFunc();
                 break;
@@ -510,9 +504,7 @@ public class ALRemoteControllerView extends RelativeLayout
             case R.id.land_btn:
                 landBtnFunc();
                 break;
-//            case R.id.goTo_btn:
-//                this.goToFunc();
-//                break;
+
             //-------- set Throttle ----------
             case R.id.t_minus_btn:
                 downButton();
@@ -582,28 +574,10 @@ public class ALRemoteControllerView extends RelativeLayout
             case R.id.recordBtn:
                 setRecIconVisibility();
                 break;
-//            case R.id.start_plane_detection:
-//                startPlaneDetectionAlgo_btn.setBackgroundColor(Color.GREEN);
-//
-//                gimbalController.rotateGimbalToDegree(-90);
-//                controllerImageDetection.DepthBool();
-//                startPlaneDetectionAlgo();
-//                break;
-
-//            case R.id.start_yolo:
-//                startObjectDetectionAlgo_btn.setBackgroundColor(Color.GREEN);
-//
-//                gimbalController.rotateGimbalToDegree(-45);
-//                startObjectDetectionAlgo();
-//                break;
 
             case R.id.guardian:
                 toggleMovementDetection();
                 break;
-
-//            case R.id.startLandingAlgo:
-//                startLandingAlgo();
-//                break;
 
             case R.id.gimbal_pitch_update:
 //                ToastUtils.setResultToToast(String.valueOf(Float.parseFloat(gimbal.getText().toString())));
@@ -640,6 +614,7 @@ public class ALRemoteControllerView extends RelativeLayout
             toggleMovementDetectionEnd();
         } else {
             // Start movement detection
+            gimbalController.rotateGimbalToDegree(-45);
             toggleMovementDetectionStart();
 
         }

### 2024-10-23 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/ControllerImageDetection.java

@@ -41,8 +41,6 @@ import java.util.concurrent.Executors;
 
 public class ControllerImageDetection {
 
-    // depth map python view
-
     private static final String TAG = ControllerImageDetection.class.getSimpleName();
     private static final double MAX_VELOCITY = 0.5; // Maximum velocity in m/s
     private static final double DEADBAND = 0.05; // Deadband in meters
@@ -163,7 +161,7 @@ public class ControllerImageDetection {
 
         this.pitchPID = new VLD_PID(p, i, d, max_i);
         this.throttlePID = new VLD_PID(p, i, d, max_i);
-        this.landingAlgorithm = new LandingAlgorithm(pitchPID, throttlePID);
+        this.landingAlgorithm = new LandingAlgorithm(pitchPID);
 
     }
 
@@ -252,42 +250,6 @@ public class ControllerImageDetection {
             }
         }
     }
-
-//    public ControlCommand alignAndLand(Mat imgToProcess) {
-//        long currTime = System.currentTimeMillis();
-//        double dt = (currTime - prevTime) / 1000.0;
-//        prevTime = currTime;
-//
-//        // Detect the line and get the center of the line segment
-//        Point[] detectedLine = trackLine.trackSelectedLineUsingOpticalFlow(imgToProcess);
-//        if (detectedLine == null) {
-//            return stayOnPlace();  // Hover if no line is detected
-//        }
-//
-//        // Calculate vertical distance to center the line horizontally in the image
-//        double lineCenterY = (detectedLine[0].y + detectedLine[1].y) / 2.0;
-//        double centerY = imageHeight / 2.0;
-//        double yOffset = lineCenterY - centerY;
-//
-//        // If the line is centered vertically within a small threshold
-//        if (Math.abs(yOffset) < 5) {
-//            // Move forward by the distance equal to the altitude and land
-//            double altitude = dataFromDrone.getAltitudeBelow();
-//            showToast("Moving forward by altitude distance and landing.");
-//            ControlCommand moveForwardCommand = landingAlgorithm.moveForwardByDistance(altitude, dt, imgToProcess);
-//
-//            if (moveForwardCommand.getPitch() == 0 && moveForwardCommand.getRoll() == 0 && moveForwardCommand.getVerticalThrottle() == 0) {
-//                flightControlMethods.land(toggleMovementDetection, this::stopEdgeDetection);
-//                return null;
-//            }
-//
-//            return moveForwardCommand;
-//        } else {
[…]

### 2024-10-23 app/src/main/java/com/dji/sdk/sample/demo/accurateLandingController/LandingAlgorithm.java

@@ -10,112 +10,29 @@ import static com.dji.sdk.sample.internal.utils.ToastUtils.showToast;
 
 public class LandingAlgorithm {
 
-    private double targetDistance = 0.03;  // Target distance of 3 cm before the line
-    private double currentVelocity = 0.01;  // Starting velocity
     private double maxVelocity = 1.0;  // Cap the maximum velocity
 
-    private double cumulativeDistance = 0;  // Track the distance traveled
-    private double minVelocity = 0.005;  // Minimum safe velocity
-    private double accelerationRate = 0.02;  // Rate to increase velocity
-    private double decelerationThreshold = 0.1;  // Distance where deceleration begins
     private double initialDistance = 0;  // Stores initial distance to the line
 
     private VLD_PID pitchPID;
-    private VLD_PID throttlePID;
 
-    // Constructor to initialize VLD_PID objects
-    public LandingAlgorithm(VLD_PID pitchPID, VLD_PID throttlePID) {
+    public LandingAlgorithm(VLD_PID pitchPID) {
         this.pitchPID = pitchPID;
-        this.throttlePID = throttlePID;
     }
 
-
-    public ControlCommand moveForward(double dt, Mat imgToProcess) {
-        float pitchCommand = (float) pitchPID.update(0.05, dt, 1.0);  // Example constant speed forward
-        Imgproc.putText(imgToProcess, "(1) Moving Forward", new Point(imgToProcess.cols() / 2.0, imgToProcess.rows() / 2.0),
-                Imgproc.FONT_HERSHEY_SIMPLEX, 1, new Scalar(0, 255, 0), 2);
+    public ControlCommand moveForward(double dt) {
+        float pitchCommand = (float) pitchPID.update(0.05, dt, 1.0);  // Constant speed forward
         return new ControlCommand(pitchCommand, 0, 0);
     }
 
-//    public ControlCommand moveForwardByDistance(double targetDistance, double dt, Mat imgToProcess) {
-//        // Calculate remaining distance to target
-//        double remainingDistance = targetDistance - cumulativeDistance;
-//
-//        // Stop if we’re within the 3 cm tolerance
-//        if (remainingDistance <= 0.03) {
-//            // Reset cumulative distance for next movement
-//            cumulativeDistance = 0;
[…]

### 2024-10-26 Article/rexi_main_new.tex
New article format

--- 2024-10-21 Article/Article.tex
@@
-\documentclass[3p,times]{elsarticle}
+\documentclass[unnumsec,webpdf,modern,large]{mam-authoring-template}%
+
 \usepackage[utf8]{inputenc}
-
 \usepackage{amssymb,amsmath,latexsym}
@@
 \usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{pgfplots}
-\usepackage{array}
+% \usepackage[noend]{algpseudocode}
+% \usepackage{pgfplots}
+% \usepackage{array}
+\usepackage{anyfontsize}
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
@@
 \usepackage{subcaption}
-\pgfplotsset{compat=newest}
+% \pgfplotsset{compat=newest}
 %\usepackage{authblk}
-\usepackage{multirow}
-
+% \usepackage{multirow}
+\usepackage{url}
 \usepackage[outdir=./]{epstopdf}   
@@
 
-%\pagecolor[rgb]{0.25,0.25,0.25} %black
-%\color[rgb]{0.9,0.9,0.9} %grey
+% \graphicspath{{Fig/}}
 
-\usepackage{ecrc}
+% line numbers
+%\usepackage[mathlines, switch]{lineno}
+%\usepackage[right]{lineno}
 
-\makeatletter %% <- make @ usable in command sequences
-\newcount\SOUL@minus
-\makeatother  %% <- revert @
-
-%% The ecrc package defines commands needed for running heads and logos.
-%% For running heads, you can set the journal name, the volume, the starting page and the authors
-
-%% set the volume if you know. Otherwise `00'
-\volume{00}
-
-%% set the starting page if not 1
-\firstpage{1}
-
-\setlength{\textfloatsep}{5pt}
-%% Give the name of the journal
-\journalname{Computer Speech and Language}
-
-%% Give the author list to appear in the running head
-%% Example \runauth{C.V. Radhakrishnan et al.}
-\runauth{Anidjar et al.}
-
-%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
-%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
-%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
-%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
-
-%% Give the abbreviation of the Journal.
-\jid{procs}
-
-%% Give a short journal name for the dummy logo (if needed)
-\jnltitlelogo{Speech Recognition}
-
-%% Hereafter the template follows `elsarticle'.
-%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
-
-%% Elsevier CRC generally uses a numbered reference style
-%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
-%% If using BibTeX, use the style file elsarticle-num.bst
-
-%% End of ecrc-specific commands
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newcommand\MyBox[2]{
-  \fbox{\lower0.75cm
-    \vbox to 1.7cm{\vfil
-      \hbox to 1.7cm{\hfil\parbox{1.4cm}{#1\\#2}\hfil}
-      \vfil}%
-  }%
-}
+% \theoremstyle{thmstyleone}%
+% \newtheorem{theorem}{Theorem}%  meant for continuous numbers
+% %%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
+% %% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
+% \newtheorem{proposition}[theorem]{Proposition}%
+% %%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+% \theoremstyle{thmstyletwo}%
+% \newtheorem{example}{Example}%
+% \newtheorem{remark}{Remark}%
+% \theoremstyle{thmstylethree}%
+% \newtheorem{definition}{Definition}
 
@@
 
-\begin{frontmatter}
+\firstpage{1}
 
-\title{Vision-Based Automatic Landing of Drones}
+\subtitle{Final Project for B.Sc. Degree in Computer Science}
 
-\author[a,b,c,d]{Or Haim Anidjar\corref{cor1}}
-\ead{orhaim@ariel.ac.il}
+\title[Accurate Landing of Drones]{Vision-Based Automatic Accurate Landing of Drones}
 
-\author[a]{Moria Grohar}
-\ead{moriagro@gmail.com}
+\author[1,$\ast$]{Shirel Zecharia}
+\author[2]{Moria Grohar}
 
-\author[a]{Shirel Turgeman}
-\ead{shirel.zz10@gmail.com}
+% \authormark{Author Name et al.}
 
-% \author[a]{Adi Peisach}
-% \ead{adi.peisach@gmail.com}
+\address[1]{\orgdiv{School of Computer Science}, \orgname{Ariel University}, \orgaddress{\street{Golan Heights 1}, \postcode{4077625}, \state{Ariel}, \country{Israel}}}
 
-\author[a, b, c]{Boaz Ben-Moshe}
-\ead{benmo@ariel.ac.il}
+\corresp[$\ast$]{Project Mentors: Boaz Ben-Moshe, School of Computer Science, Ariel University; 
+ Or Haim Anidjar, School of Computer Science, Ariel University}
 
-\address[a]{School of Computer Science, Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}
-
-\address[b]{Ariel Cyber Innovation Center, Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}
-
-\address[c]{Kinematics and Computational Geometry Lab (K\&CG), Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}
-
-\address[d]{Data Science and Artificial Intelligence Research Center, Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}
-
-\cortext[cor1]{Corresponding author: Or Haim Anidjar, School of Computer Science, Ariel University, Golan Heights 1, 4077625, Ariel, Israel.}
-
-\begin{abstract}
-This article introduces a platform designed to enable precise landings on the edge of rooftops, facilitating operations at boundary locations.
+\abstract{This article introduces a platform designed to enable precise landings on the edge of rooftops, facilitating operations at boundary locations.
 The platform integrates voice recognition capabilities for activation, eliminating reliance on manual button controls.
@@
 Once obstacles are cleared, the drone transitions to descent mode.
-For precise landings at the edge of a rooftop, an edge detection algorithm is employed alongside a target line selection process, allowing the user to designate a specific landing line beforehand, ensuring accuracy during the final approach.
-\end{abstract}
+For precise landings at the edge of a rooftop, an edge detection algorithm is employed alongside a target line selection process, allowing the user to designate a specific landing line beforehand, ensuring accuracy during the final approach.}
 
-\begin{keyword}
-Visual-Based Landing \sep Autonomous Landing \sep Accurate Landing\sep Spoken Language Recognition.
-\end{keyword}
+\keywords{Visual-Based Landing, Autonomous Landing, Accurate Landing, Spoken Language Recognition.}
 
-\end{frontmatter}
+\maketitle
 
@@
 On the civilian side, drones are utilized for activities like environmental monitoring, weather data collection, and infrastructure inspection.
-As drones become increasingly prevalent in both sectors, ensuring their safe operation—particularly during landing—has emerged as a critical concern.\\Autonomous drone operations have rapidly advanced, yet precision landing remains a significant challenge, especially in environments where GPS signals are unreliable or unavailable.
+As drones become increasingly prevalent in both sectors, ensuring their safe operation—particularly during landing—has emerged as a critical concern .\\Autonomous drone operations have rapidly advanced, yet precision landing remains a significant challenge, especially in environments where GPS signals are unreliable or unavailable.
 GPS signals can be easily disrupted by various factors: (a) weather conditions and sunspots may weaken signals, although they typically do not hinder positioning; (b) electromagnetic interference from sources like radios and strong magnetic fields can cause varying degrees of disruption; (c) signal strength diminishes under shelters such as buildings, vehicles, insulation materials, trees, and metal components; and (d) high-rise buildings and dense urban areas can severely impact GPS signal quality.
@@
 
-\subsection{Authors Contribution}
-We propose a visual processing framework that enables the drone to autonomously land by utilizing object (obstacle) detection and edge detection.
+\section{Authors Contribution}\label{sec2}
+We propose a visual processing framework that enables the drone to land autonomously by utilizing object (obstacle) detection and edge detection.
 Our approach is tested on a DJI drone equipped with a standard camera, using the DJI SDK for implementation on Android devices.
 Additionally, we have implemented a "guard" mode in the app — a button that, when activated, is designed to detect movement (such as people, cars, etc.) and send alerts.
-The system's robustness is further enhanced by incorporating basic voice commands through a speech recognition module, meeting the requirements outlined by MAFAT.\\
+The system's robustness is further enhanced by incorporating basic voice commands through a speech recognition module, meeting the requirements outlined by MAFAT.
 
-\section{Related Work} \label{sec:related}
+\section{Related Work}\label{sec3}
 \subsection{Obstacle Avoidance}
@@
 
+\subsection{Vision-Based Autonomous Landing for the UAV}
+In their review of vision-based autonomous UAV landings \cite{aerospace9110634} categorize landing scenarios into static, dynamic, and complex.
+Static landings often use cooperative targets like barcodes or fiducial markers for accurate positioning, while dynamic landings include vehicle- and ship-based platforms.
+The authors emphasize the challenges of real-time processing, limited onboard resources, and UAV maneuverability, noting that complex environments remain a significant research focus, with future work aimed at multi-sensor fusion and algorithmic adaptability.
+
 \subsection{An improved Canny edge detection algorithm}
@@
 \section{Drone Control Mechanisms} \label{sec:mechanisms}
+\subsection{Drone Control Parameters}
 The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle. 
-These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.\\
+These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.
 \begin{description}
@@
 
-\newpage \section{Algorithm Design} \label{sec:algorithm}
+\subsection{Remote Controller Overview} \label{sec:RemoteControllerOverview}
+
+The remote controller is crucial for operating a drone, allowing the pilot to manage flight characteristics effectively. Key features include:
+
+\begin{description}
+\item $\bullet$ Joysticks - The left joystick controls throttle and yaw, while the right joystick manages pitch and roll, enabling intuitive movement and orientation.
+
+\item $\bullet$ Buttons and Switches - Various buttons activate functions such as takeoff, landing, camera capture, and flight mode adjustments, enhancing operational versatility.
+
+\item $\bullet$ Display Screen - Many controllers include a screen or connect to mobile devices to provide real-time telemetry, such as altitude, speed, and battery status, improving situational awareness.
+
+\item $\bullet$ Communication Protocol - The controller communicates with the drone via RF signals, ensuring reliable connectivity and minimal latency during flight.
+
+\end{description}
+
+\subsection{Drone Sensors} \label{sec}
+
+Drones utilize various sensors to enhance stability, navigation, and functionality during flight. Key sensors include:
+
+\begin{description}
+
+\item $\bullet$ Barometers - Measure atmospheric pressure to determine altitude.
+By monitoring changes in pressure, barometers help the drone maintain a steady altitude, which is essential for stable flight and landing.
+
+\item $\bullet$ GPS (Global Positioning System) - Provides location data, enabling the drone to navigate to specific coordinates, maintain its position, and return to home automatically.
+GPS is vital for autonomous flight operations.
+
+\item $\bullet$ Vision Sensors - Include cameras and optical flow sensors, allowing the drone to detect and track objects, recognize surfaces, and assist in navigation by analyzing visual data.
+These sensors are essential for tasks like object avoidance and following lines during autonomous flight.
+
+\item $\bullet$ Ultrasonic Sensors - Measure distance to the ground using sound waves, aiding in altitude control and collision avoidance during low-altitude flights.
+
+\end{description}
+
+Together, these sensors provide the necessary data for the drone's flight controller to make real-time adjustments, ensuring stable and responsive flight even in challenging conditions.
+
+This combination of controls and displays enhances the pilot's ability to maneuver the drone accurately and safely.
+
+\section{Experimental Setup} \label{Experimental Setup}
+
+\subsection{Hardware Used:}
+For all flight operations, the DJI Mavic Air 2 was employed, utilizing its standard camera and onboard sensors.
+The drone's ability to control yaw, pitch, roll, throttle, and altitude played a crucial role in the testing and experiment execution.
+
+\subsection{Testing Environment}
+
+The experiments were conducted in both indoor and outdoor environments.
+For outdoor tests, the drone was operated in real-world conditions, including on the ground and atop a table, to simulate different elevation scenarios.
+Additionally, the DJI Mavic Air 2 was tested in varying weather conditions, including strong winds and sunny days, to assess its performance under challenging conditions.\\
+To supplement the real-world tests, a simulator was employed to thoroughly evaluate the drone’s behavior and command responsiveness in a controlled, non-real-world-based environment.
+This simulation allowed us to test the system's reaction to flight commands, such as takeoff, landing, edge detection, and obstacle avoidance, in a reproducible setting without the risks associated with physical testing.\\
+By testing in both simulated and real environments, the drone's flight stability and command accuracy were evaluated under diverse conditions, ensuring robustness and reliability in practical applications.
+
+\section{Algorithm Design} \label{sec:algorithm}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{landingMainExplenation.png}  % Reduced the size here
+    \caption{Landing view screen while running the app.}
+    \label{fig:landingMainExplenation.}
+\end{figure}
 Our proposed algorithm for autonomous drone landing consists of three key components: Target Line Selection, Flight Control, and Object Detection.
 Each part contributes to the overall reliability and precision of the landing process, ensuring safe navigation and obstacle avoidance.
-
+Our algorithm utilizes the camera mounted on a gimbal angled at 45°.
 \begin{figure}[H]
     \centering
-    \includegraphics[width=0.7\textwidth]{Schematic_for_automatic_landing.png}  % Reduced the size here
+    \includegraphics[width=0.5\textwidth]{Schematic_for_automatic_landing.png}  % Reduced the size here
     \caption{Schematic for automatic landing.}
@@
 Through experimental measurements, we identified a blind spot between the drone's final visible position of the line and its actual location in reality.
-To compensate for this, the algorithm calculates the necessary adjustment and issues a final pitch command, ensuring that the drone reaches the correct position relative to the target line.
+To compensate for this, the algorithm uses the ratio $$ R=\frac{h}{d}$$, where $h$ is the drone’s height and $d$ is the blind spot distance, to calculate the necessary adjustment. 
+For diagonal movement at a 45° angle, the pitch (horizontal) and throttle (vertical) inputs must result in equal movement.
+The blind spot ratio R is used to balance them: $$R = \frac{throttle\_value}{pitch\_value}$$ Here, the throttle value is adjusted according to the drone's height, ensuring accurate diagonal movement and blind spot compensation.
+A final pitch command ensures the drone reaches the correct position relative to the target line.
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{Blind Spot Area.png}  % Reduced the size here
+    \includegraphics[width=0.5\textwidth]{Blind Spot Area.png}  % Reduced the size here
     % \caption{Schematic for automatic landing.}
@@
 In this mode, the system continuously monitors the surrounding environment for movement.\\
-
 Movement detection is implemented using the YOLO (You Only Look Once) object detection framework, which enables real-time identification of objects such as people, vehicles, or other moving entities.
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{movementDetect.jpeg}  % Reduced the size here
+    \includegraphics[width=0.5\textwidth]{movementDetect.png}  % Reduced the size here
     % \caption{Guardian mode activated.}
@@
 \item $\bullet$ Edge detection - Activates the edge detection algorithm, allowing the system to identify and process edges for navigation or object tracking.
+\item $\bullet$ Movement detection (Guard Mode) - Activates a security or surveillance mode where the drone monitors for movement in its environment and triggers alerts or actions based on detected motion.
+\subitem $\bullet$ Start movement detection - Begins monitoring the environment for movement.
+\subitem $\bullet$ Stop movement detection - Disables the movement detection and returns to normal operation.
+\end{description}
+This combination of commands allows users to control the drone in various situations, from basic navigation to more advanced functionality, such as edge detection and movement detection for security or surveillance purposes.
 
-\end{description}
-
-% \section{Discussion} \label{sec:discussion}
-
-% Advancements in language recognition technologies have been noteworthy, yet they confront several challenges and limitations. This discussion highlights some of the prevalent issues:
-
-% \begin{enumerate}
-
-%     \item \textbf{Linguistic Ambiguity.} Distinguishing between languages with shared linguistic traits
-
-%     \item \textbf{Code-Switching Phenomenon.} In multilingual settings,
-
-% \end{enumerate}
-
-\newpage \section{Future Work} \label{sec:future}
+\section{Future Work} \label{sec:future}
 An important area for future improvement is the algorithm's ability to handle wind conditions, particularly in outdoor environments and at higher altitudes.
 While the current implementation performs reliably in controlled settings, real-world scenarios—such as fluctuating wind speeds and changing directions—pose significant challenges to the drone's stability and landing accuracy.
-Specifically, turbulence at great heights can disrupt the drone's trajectory, leading to deviations from the intended flight path and reducing the precision of both target line tracking and landing position.
-
+Specifically, turbulence at great heights can disrupt the drone's trajectory, leading to deviations from the intended flight path and reducing the precision of both target line tracking and landing position.\\
 To address these challenges, we plan to enhance the algorithm by integrating real-time wind compensation techniques.
 This improvement will involve adapting the flight control module to account for external forces, using sensor and visual data to counteract wind disturbances, and dynamically adjusting the drone's movements.
-Enhancing wind handling will enable the algorithm to perform more reliably across a wider range of scenarios, ensuring consistent operation in varying environmental conditions.
-
+Enhancing wind handling will enable the algorithm to perform more reliably across a wider range of scenarios, ensuring consistent operation in varying environmental conditions.\\
 Additional future work includes transitioning the speech recognition system from an online to an offline model, which will improve reliability by ensuring consistent functionality without internet access.
@@
 \section{Conclusion}
-In this work, we presented a novel approach for autonomous drone landing using a visual-based framework that eliminates the need for GPS.
-Our algorithm, tested on a DJI drone equipped with a standard camera, successfully integrates object detection, edge detection, and flight control to enable precise landings.
+In this work, we presented a novel approach for autonomous drone landing using a visual-based framework that eliminates the need for GPS.\\
+Our algorithm, tested on a DJI drone equipped with a standard camera, successfully integrates object detection, edge detection, and flight control to enable precise landings. \\
 The system's performance in controlled environments demonstrates its effectiveness, especially in scenarios where GPS signals are unreliable or unavailable.\\
-
-However, there are still challenges to address, particularly in handling unpredictable wind conditions and ensuring the system’s reliability in diverse outdoor environments.
+However, there are still challenges to address, particularly in handling unpredictable wind conditions and ensuring the system’s reliability in diverse outdoor environments.\\
 Future work will focus on improving the algorithm’s robustness in real-world scenarios and enhancing its functionality through additional features such as offline speech recognition and plane recognition algorithms for safer and more autonomous landings.\\
-
 The combination of these developments will pave the way for safer, more reliable, and efficient drone operations in a wide variety of applications, from urban package delivery to military surveillance missions.
 
-% \bibliographystyle{model5-names}\biboptions{authoryear}
-% \bibliography{main}
 \bibliographystyle{plain}

### 2024-10-26 Article/rexi_main_new.tex
Modify introduction and fixed pictures

@@
 
-\corresp[$\ast$]{Project Mentors: Boaz Ben-Moshe, School of Computer Science, Ariel University; 
- Or Haim Anidjar, School of Computer Science, Ariel University}
+\corresp[$\ast$]{Project Mentors: Boaz Ben-Moshe, School of Computer Science, Ariel University; Or Haim Anidjar, School of Computer Science, Ariel University}
 
@@
 Drones are valued for their simple yet effective design, ease of operation, flexibility, and cost-efficiency, making them versatile tools in both military and civilian domains.
-In military operations, they play crucial roles in tasks such as tactical reconnaissance, territorial surveillance, and target acquisition.
+In military operations, drones play pivotal roles in tasks such as tactical reconnaissance, territorial surveillance, and target acquisition.
+In surveillance missions, accurate landing is especially critical, as drones must often be deployed to specific vantage points—such as rooftops or elevated positions—where stable operation is essential for continuous monitoring of target areas.\\
 On the civilian side, drones are utilized for activities like environmental monitoring, weather data collection, and infrastructure inspection.
-As drones become increasingly prevalent in both sectors, ensuring their safe operation—particularly during landing—has emerged as a critical concern .\\Autonomous drone operations have rapidly advanced, yet precision landing remains a significant challenge, especially in environments where GPS signals are unreliable or unavailable.
+As drones become increasingly prevalent in both sectors, ensuring their safe and precise landing—particularly in challenging environments—has emerged as a critical concern.
+In surveillance operations, an accurate landing ensures that drones can be positioned optimally to capture and monitor sensitive areas over extended periods, thus reducing the need for human intervention and minimizing the risks associated with miscalculation during deployment.\\
+Autonomous drone operations have rapidly advanced, yet precision landing remains a significant challenge, especially in environments where GPS signals are unreliable or unavailable.
 GPS signals can be easily disrupted by various factors: (a) weather conditions and sunspots may weaken signals, although they typically do not hinder positioning; (b) electromagnetic interference from sources like radios and strong magnetic fields can cause varying degrees of disruption; (c) signal strength diminishes under shelters such as buildings, vehicles, insulation materials, trees, and metal components; and (d) high-rise buildings and dense urban areas can severely impact GPS signal quality.
 Traditional drone landing methods often rely on GPS, which proves inadequate in urban or indoor settings.
-This limitation poses significant challenges for applications requiring precise landings, such as urban package delivery, infrastructure inspection, and emergency response.
+This limitation poses significant challenges for applications requiring precise landings, such as military surveillance, urban package delivery, infrastructure inspection, and emergency response.
 As a result, there is a critical need to develop autonomous positioning and flight control systems for drones that do not rely on GPS signals.\\
 This research addresses these challenges by developing a visual-based landing system that enhances accuracy and safety.
-Our approach enables drones to autonomously identify and land on planar surfaces, such as rooftops, relying solely on visual data from the onboard camera.
-By eliminating the need for additional sensors or external data inputs, this system offers a robust solution for autonomous landings in complex environments.
+Our approach enables drones to autonomously identify and land on strategic surfaces, such as rooftops, relying solely on visual data from the onboard camera.
+By eliminating the need for additional sensors or external data inputs, this system offers a robust solution for autonomous landings in complex environments, ensuring the drone is precisely positioned for effective surveillance and monitoring.
 
@@
 These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.
-\begin{description}
-\item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
-\item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
-\item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
-\item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
-\end{description}
+
+\textbf{Yaw} - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
+
+\textbf{Pitch} - adjusts the forward and backward tilt, moving the drone in those directions.
+
+\textbf{Roll} - manages side-to-side tilt, shifting the drone left or right.
+
+\textbf{Throttle} - regulates altitude by increasing or decreasing the drone’s lift.
 
@@
 
-\begin{description}
-\item $\bullet$ Joysticks - The left joystick controls throttle and yaw, while the right joystick manages pitch and roll, enabling intuitive movement and orientation.
+(a) Joysticks - The left joystick controls throttle and yaw, while the right joystick manages pitch and roll, enabling intuitive movement and orientation.
 
-\item $\bullet$ Buttons and Switches - Various buttons activate functions such as takeoff, landing, camera capture, and flight mode adjustments, enhancing operational versatility.
+(b) Buttons and Switches - Various buttons activate functions such as takeoff, landing, camera capture, and flight mode adjustments, enhancing operational versatility.
 
-\item $\bullet$ Display Screen - Many controllers include a screen or connect to mobile devices to provide real-time telemetry, such as altitude, speed, and battery status, improving situational awareness.
+(c) Display Screen - Many controllers include a screen or connect to mobile devices to provide real-time telemetry, such as altitude, speed, and battery status, improving situational awareness.
 
-\item $\bullet$ Communication Protocol - The controller communicates with the drone via RF signals, ensuring reliable connectivity and minimal latency during flight.
-
-\end{description}
+(d) Communication Protocol - The controller communicates with the drone via RF signals, ensuring reliable connectivity and minimal latency during flight.
 
@@
 By testing in both simulated and real environments, the drone's flight stability and command accuracy were evaluated under diverse conditions, ensuring robustness and reliability in practical applications.
-
-\section{Algorithm Design} \label{sec:algorithm}
+\subsection{Application View}
 \begin{figure}[H]
     \centering
-    \includegraphics[width=0.5\textwidth]{landingMainExplenation.png}  % Reduced the size here
+    \includegraphics[width=0.55\textwidth]{landingMainExplenation.png}  % Reduced the size here
     \caption{Landing view screen while running the app.}
@@
 \end{figure}
+\section{Algorithm Design} \label{sec:algorithm}
+
 Our proposed algorithm for autonomous drone landing consists of three key components: Target Line Selection, Flight Control, and Object Detection.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Schematic_for_automatic_landing.png}  % Reduced the size here
+    \includegraphics[width=0.48\textwidth]{Schematic_for_automatic_landing.png}  % Reduced the size here
     \caption{Schematic for automatic landing.}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{Blind Spot Area.png}  % Reduced the size here
-    % \caption{Schematic for automatic landing.}
+    \includegraphics[width=0.5\textwidth]{Blind Spot Area.png}
+    \caption{Blind Spot Area.}
     \label{fig:Blind Spot Area.}
@@
 Each recognized command triggers a specific action in the drone. The key commands and their associated actions are:
-\begin{description}
-\item $\bullet$ Takeoff - Initiates the drone's takeoff sequence, lifting it to a designated altitude for hover.
-\item $\bullet$ Land - Initiates the landing sequence, lowering the throttle for a controlled descent until the drone reaches the ground.
-\item $\bullet$ Stop - Halts any current movement, keeping the drone stationary in hover mode.
-\item $\bullet$ Move up - Increases the throttle to elevate the drone vertically.
-\item $\bullet$ Move down - Decreases the throttle, causing the drone to descend.
-\item $\bullet$ Start recording - Begins video recording using the drone's camera.
-\item $\bullet$ Stop recording - Stops the video recording and saves the footage.
-\item $\bullet$ Edge detection - Activates the edge detection algorithm, allowing the system to identify and process edges for navigation or object tracking.
-\item $\bullet$ Movement detection (Guard Mode) - Activates a security or surveillance mode where the drone monitors for movement in its environment and triggers alerts or actions based on detected motion.
-\subitem $\bullet$ Start movement detection - Begins monitoring the environment for movement.
-\subitem $\bullet$ Stop movement detection - Disables the movement detection and returns to normal operation.
-\end{description}
+
+(a) \textbf{Takeoff} - Initiates the drone's takeoff sequence, lifting it to a designated altitude for hover.
+
+(b) \textbf{Land} - Initiates the landing sequence, lowering the throttle for a controlled descent until the drone reaches the ground.
+
+(c) \textbf{Stop} - Halts any current movement, keeping the drone stationary in hover mode.
+
+(d) \textbf{Move up} - Increases the throttle to elevate the drone vertically.
+
+(e) \textbf{Move down} - Decreases the throttle, causing the drone to descend.
+
+(g) \textbf{Start recording} - Begins video recording using the drone's camera.
+
+(h) \textbf{Stop recording} - Stops the video recording and saves the footage.
+
+(i) \textbf{Edge detection} - Activates the edge detection algorithm, allowing the system to identify and process edges for navigation or object tracking.
+
+(j) \textbf{Movement detection (Guard Mode)} - Activates a security or surveillance mode where the drone monitors for movement in its environment and triggers alerts or actions based on detected motion.
+
+(k) \textbf{Start movement detection} - Begins monitoring the environment for movement.
+
+(l) \textbf{Stop movement detection} - Disables the movement detection and returns to normal operation.
+
 This combination of commands allows users to control the drone in various situations, from basic navigation to more advanced functionality, such as edge detection and movement detection for security or surveillance purposes.
